\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.23\linewidth}>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}}
\toprule
Baseline family & Task alignment & Fairness control & Residual risk & Usable claim \\
\midrule
Direct algebraic and ESOP baselines & Same bit-flip Boolean oracle target and the same logical resource model. & Matched $n\leq6$ functions, complete truth-table checks, identical score coefficients, and paired per-function comparisons. & These baselines are representation-level constructions, not mature external compilers. & Primary evidence for lower T-count and weighted score under the paper's own oracle model. \\
SSHR-H and SSHR-I & Same small Boolean-function oracle setting, but with a CNOT-oriented parallelotope search objective. & Matched functions and resource extraction; SSHR-I timeout rows are separated from completed rows. & SSHR is optimized for CNOT structure and small n, so it is a counterpoint rather than the method's design parent. & \method{} improves score and T-count while SSHR remains the strongest CNOT reference. \\
ABC/\allowbreak{}BDD and exported logic networks & Same exported Boolean functions, evaluated through logical AIG/\allowbreak{}XAG/\allowbreak{}LUT/\allowbreak{}BDD resource proxies. & Rows with errors, skips, or failed truth-table checks are excluded; paired comparisons use matched names. & Network-level counts are proxies and do not include reversible garbage management or quantum routing. & Mature classical logic optimization does not by itself remove the T/\allowbreak{}score advantage. \\
ROS-style LUT and XAG/\allowbreak{}AIG/\allowbreak{}API probes & Same benchmark functions pass through LUT, XAG, AIG, and Caterpillar API probes with export/\allowbreak{}readback checks where available. & The LUT proxy includes best-K, line-aware reselection, and an executable garbage-budget frontier; mockturtle, CirKit, and Caterpillar use official source/\allowbreak{}toolchain/\allowbreak{}API paths and row-level correctness checks. & These are not full ROS SAT garbage-management optimizers or hardware-mapped reversible flows. & The advantage persists beyond self-written baselines, with CirKit and Caterpillar exposing real CNOT/\allowbreak{}depth tradeoffs. \\
Published STG optimum-library counterpoint & The public n=4/\allowbreak{}5 STG representatives are matched to locally synthesized rows by truth-table hex. & Published T-count, T-depth, and qubit optima remain separate objectives; local rows are verified on the same truth tables and are not presented as a rerun of the optimum-library solver. & The published optima are precomputed tiny-function references with decomposition assumptions that do not define the paper's larger-n search setting. & This slice is a non-win boundary showing that the paper does not hide stronger tiny-function optimum references. \\
Legacy RevKit CLI exact-oracle portfolio & Each function is embedded as the exact reversible permutation $(x,y)\mapsto(x,y\oplus f(x))$. & TBS, DBS, and RMS are all run and reduced to a per-function best-score portfolio. & CNOT and depth are derived from Toffoli-control distributions; RevKit uses fewer auxiliary lines on most rows. & A genuine reversible-synthesis probe still favors \method{} on T-count and score, but not on line count. \\
Phase/\allowbreak{}\rz{} baselines and learned shortlist & Same Boolean functions are evaluated as phase-oracle or affine-\fprm{} phase-search instances. & Rows are verified up to global phase; learned shortlists are checked against same-budget random controls and wide exact search. & The branch is a logical \rz{}/\allowbreak{}phase proxy and does not output rotation-synthesis sequences. & The search framing extends to verified phase/\allowbreak{}\rz{} proxies, but it is not a finished Clifford+T compiler. \\
AI/\allowbreak{}search-control ablations & Each ablation reuses matched functions and, where causal attribution is claimed, the same candidate pool or search budget. & No-\mcts{}, beam, \mcts{}, Pareto, learned-prior, same-budget random-prior, random-depth, held-out, and independent-seed controls are reported with quality and runtime separated. & The controls span several search branches and include small or runtime-negative learned effects, so they do not identify one universal deep-RL effect. & The controls support bounded attribution to \mcts{}, Pareto selection, learned ranking, and budget allocation rather than to representation alone. \\
High-dimensional symbolic and bridge checks & Large term-set instances and $n=21$--$30$ bridge functions test the same emitted logical oracle semantics. & Symbolic \anf{}/\allowbreak{}circuit checks cover all reported high-dimensional rows; bridge slices add complete truth-table checks. & Complete truth-table enumeration is limited to bridge slices and generated functions. & The large-scale evidence supports semantic correctness and scaling of the logical search, not exhaustive high-dimensional optimality. \\
Trade-off and resource-sensitivity audits & Matched verified functions are compared through the same logical resource vectors before any weighted score is interpreted. & Four-resource dominance excludes the weighted score, and coefficient sweeps recompute every matched method pair under the same declared resource profile. & All resources remain logical-layer proxies before routing, native-gate mapping, noise, and fault-tolerant factory costs. & The method occupies a strong T-count and weighted-score region with explicit CNOT, depth, ancilla, and coefficient-sensitivity counterpoints. \\
\bottomrule
\end{tabularx}
