\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.21\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.18\linewidth}}
\toprule
Family & Input/verifier contract & Evidence coverage & Supported use & Boundary \\
\midrule
Same-task Boolean-oracle baselines & Matched truth-table Boolean functions in the bit-flip oracle form. Complete truth-table correctness on small functions plus paired-name filtering. & Internal logical baselines: 1770/1770; Exported SSHR/ABC/BDD extension: 1416/1416 & Lower T-count and weighted score on matched logical bit-flip oracle rows. & No universal CNOT, depth, line-count, mapped-depth, or global-optimality claim. \\
SSHR geometric counterpoint & The same $n\leq6$ Boolean functions are compared against SSHR-H and SSHR-I rows where available. SSHR rows are consumed only after row-level correctness and timeout accounting. & Internal logical baselines: 1770/1770; Exported SSHR/ABC/BDD extension: 1416/1416 & The proposed search has lower T-count and weighted score while SSHR remains CNOT-competitive. & Do not claim CNOT dominance over SSHR or full reproduction of every SSHR random experiment. \\
External logic-network probes & Exported truth tables or \anf{}/XAG/AIG/LUT encodings of the same benchmark functions. Tool outputs are checked through truth-table, BLIF, Verilog, or API readback where available. & ROS-style LUT proxy: 309/309 best rows; 927/927 K-sweep rows; 927/927 garbage-proxy rows; 1059/1059 garbage-budget rows; mockturtle KLUT-to-XAG probe: 241/241; Caterpillar XAG API probe: 177/177 best rows; 531/531 strategy rows; CirKit AIG/MC probe: 241/241 & The T/score advantage is not only an artifact of self-written algebraic baselines. & Not a full ROS SAT garbage-management, reversible-emission, or hardware-mapped comparison. \\
Published tiny-function optima & Public n=4/5 STG spectral representatives are matched by truth-table hex. Rows are checked as a published-counterpoint slice, not as a reproduced optimizer. & Published STG optimum-library counterpoint: 270/270 & The method improves local direct baselines on this slice but does not beat STG optima. & No claim of beating published STG T-count, T-depth, or qubit optima. \\
RevKit exact-oracle probe & Each function is embedded as the exact permutation $(x,y)\mapsto(x,y\oplus f(x))$. RevKit portfolio rows are checked through the exact-oracle permutation route. & Legacy RevKit CLI exact oracle: 708/708 & A reversible-synthesis portfolio does not remove the T-count/score advantage. & Do not claim lower auxiliary-line count, routed depth, or final mapped Clifford+T dominance. \\
Phase/\rz{} transfer branch & The same Boolean functions are evaluated as phase-oracle or affine-\fprm{} instances. Phase rows are verified up to global phase and shortlist rows against exact scoring. & RevKit phase/\rz{} branch: 531/531; Learned phase pruning: 7611/7611 & Affine search and learned shortlist pruning help a related verified phase/\rz{} proxy. & Not a final approximate-rotation or Clifford+T sequence-synthesis result. \\
AI/search-control ablations & Ablations reuse the same benchmark names, budgets, or candidate pools when applicable. Learned controls are accepted only through guarded rows, random controls, or disjoint held-out checks with explicit uncertainty gates. & derived audit rows only & \mcts{} and Pareto selection add bounded quality gains; fitted-Q control reduces optional Pareto effort at explicit score regret. & Do not claim deep reinforcement learning alone causes the full resource reduction or dominates always-on Pareto score. \\
Large-scale correctness envelope & Generated large-n term-set functions and bridge functions exercise the same emitted oracle semantics. Symbolic \anf{}/circuit verification covers scale rows; $n=21$--$30$ bridges add full truth-table checks. & High-dimensional frontier search: 2088/2088; Complete truth-table bridges: 700/700 & The emitter and verifier remain effective beyond the $n\leq6$ truth-table benchmark slice. & Not exhaustive high-dimensional truth-table benchmarking or global optimality evidence. \\
Trade-off and sensitivity rows & Matched-function resource vectors are audited independently of weighted score. Dominance and sensitivity rows are derived from verified raw comparison tables. & derived audit rows only & The method occupies a strong T/score point with explicit CNOT/depth/ancilla trade-offs. & No complete Pareto dominance or hardware-level dominance claim. \\
\bottomrule
\end{tabularx}
