\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.17\linewidth}>{\raggedright\arraybackslash}p{0.12\linewidth}>{\raggedright\arraybackslash}p{0.15\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.22\linewidth}}
\toprule
Evidence block & Scope & Verified rows & Main score result & Boundary \\
\midrule
Internal logical baselines & $n=3$--$6$ & 1770/1770 & Pareto vs direct ANF 172/1/4, -67.80\%; vs ESOP-MILP 167/3/7, -29.84\% & Same verifier/cost model; includes direct, AND-direct, ESOP beam/MILP, SSHR-H, MCTS, affine, and Pareto variants. \\
Exported SSHR/ABC/BDD extension & $n=3$--$6$ & 1416/1416 & Resource-NMCTS vs SSHR-I CNOT 172/5/0, -29.48\%; vs ABC-XAG 177/0/0, -64.15\% & SSHR-I rows use an 8 s Gurobi budget; ABC/BDD rows are logical estimates over exported truth tables. \\
ROS-style LUT proxy & $n=3$--$6$, 14, 15, 16, 18 & 309/309 best rows; 927/927 K-sweep rows; 927/927 garbage-proxy rows; 1059/1059 garbage-budget rows & Pareto vs best-K proxy 309/0/0, -84.27\% & Verified LUT and executable garbage-pressure proxies only; no official ROS SAT garbage management, reversible emission, or hardware mapping. \\
Published STG optimum-library counterpoint & n=4-5 & 270/270 & Pareto vs STG T-count optimum 0/40/14, +84.26\%; vs direct ANF on STG slice 50/4/0, -58.10\% & Public n=4/5 spectral-representative optimum-library table; this is a strong small-function counterpoint, not a reproduced ROS flow or scalable compiler baseline. \\
mockturtle KLUT-to-XAG probe & $n=3$--$6$, 14 & 241/241 & $n\leq6$ 166/11/0, -31.50\%; $n=14$ 64/0/0, -91.49\% & Official-header XAG resynthesis probe; still a logical proxy, not full ROS or reversible garbage management. \\
Caterpillar XAG API probe & $n=3$--$6$ & 177/177 best rows; 531/531 strategy rows & Pareto vs best API score 177/0/0, -47.94\%; CNOT 4/173/0, +195.18\% & Local Caterpillar logic-network API over ANF-XAG inputs; verified implementation-family performance probe, not full ROS SAT garbage management. \\
CirKit AIG/MC probe & $n=3$--$6$, 14 & 241/241 & $n\leq6$ 177/0/0, -62.34\%; $n=14$ 64/0/0, -94.46\% & AIG multiplicative-complexity probe; strongest current depth-oriented external counterpoint. \\
Legacy RevKit CLI exact oracle & $n=3$--$6$ & 708/708 & Pareto vs best-score portfolio 173/0/4, -67.28\% & Exact reversible oracle permutation; CNOT/depth are derived from Toffoli-control distributions and ancilla is a visible tradeoff. \\
RevKit phase/Rz branch & $n=3$--$6$ & 531/531 & Affine phase vs RevKit oracle\_synth 177/0/0, -65.50\% & Logical phase/Rz proxy verified up to global phase; sequence evidence is a coarse smoke check, not optimal Clifford+T synthesis. \\
Learned phase pruning & $n=3$--$6$ & 7611/7611 & Held-out n=6 rank-diverse top512 vs wide128 0/7/31, +0.00\% & Policy-pruned affine candidate ranking; evidence is held-out exact scoring, not a standalone compiler backend. \\
High-dimensional frontier search & $n=20$, 24, 28, 32, 40, 48, 56, 64 & 2088/2088 & Stage-gated vs all-depth scale 0/4/92, +0.04\% score; -25.43\% time; ultra $n=48$, 56, 64 stress 480/480 plan+circuit verified & Term-set symbolic verification with emitted-circuit ANF checks; depth frontier is a planning guard, not a hardware scheduler. \\
Complete truth-table bridges & $n=21$--$30$ & 700/700 & Bridge rows verify plan, emitted symbolic circuit, and complete truth table for $n=21$--$30$. & Bridge set is intentionally narrow because complete truth tables grow exponentially. \\
\bottomrule
\end{tabularx}
