\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.15\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.26\linewidth}}
\toprule
Target family & Role & Why meaningful & Invalid statement \\
\midrule
Same-task Boolean-oracle baselines & primary benchmark & These baselines solve the same bit-flip Boolean-oracle task or the closest small-function CNOT-oriented variant under the logical resource model. & Not evidence of universal CNOT, depth, ancilla, line-count, or hardware-mapped optimality. \\
External logic-network probes & external stress test & These probes test whether mature Boolean-network and LUT/XAG/AIG optimization already removes the apparent advantage. & Not a full ROS SAT garbage-management optimizer, reversible-emission, routing, or hardware-mapped comparison. \\
Published STG optimum-library counterpoint & small-function optimum counterpoint & This target asks whether the generic logical search beats a precomputed tiny-function optimum library; the expected use is a boundary, not a headline win. & Not evidence of beating published STG T-count, T-depth, or qubit optima. \\
Exact reversible-synthesis probe & exact reversible counterpoint & The baseline embeds each function as the exact reversible permutation and checks a genuine reversible-synthesis toolchain. & Not evidence of lower auxiliary-line count, routed depth, or final mapped Clifford+T dominance. \\
Phase/\rz{} branch & phase proxy & This branch tests whether the search framing transfers to verified logical phase/\rz{} proxy objectives. & Not a final approximate-rotation synthesis or full Clifford+T sequence. \\
AI/search-control ablations & causal control & These controls separate representation/search-space effects from \mcts{}, neural ranking, guards, and reinforcement-learned Pareto budget allocation. & Not evidence that deep reinforcement learning alone causes the full resource reduction or dominates always-on Pareto score. \\
Scaling and correctness bridges & scalability verification & These rows test whether emitted logical oracles remain verifiable beyond the small truth-table benchmark slice. & Not exhaustive high-dimensional truth-table benchmarking or optimality evidence. \\
Trade-off counterpoints & non-dominance boundary & These counterpoints keep the comparison meaningful by exposing metrics where other methods remain strong. & Not a single universal leaderboard or complete Pareto dominance claim. \\
\bottomrule
\end{tabularx}
