\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.24\linewidth}}
\toprule
Contribution & Implementation & Paper evidence & Boundary \\
\midrule
Resource-constrained Boolean-oracle search formulation & \anf{}/\fprm{} term-set state, Boolean-ring and affine actions, guarded candidate selection, symbolic circuit emission. & Fig.~\ref{fig:pipeline}; Table~\ref{tab:related-positioning} & Logical-layer oracle synthesis only; no routing, native-gate mapping, or noise model. \\
Neural/\mcts{} search with reinforcement-learned budget control & Neural action priors, \mcts{}/beam/portfolio search, Pareto archive, frontier policies, and a contextual-bandit fitted-Q controller for optional Pareto invocation. & Tables~\ref{tab:contribution}, \ref{tab:search-control-baseline-audit}, \ref{tab:learned-control-audit}, \ref{tab:mcts-budget-policy}; Fig.~\ref{fig:learned-control-summary} & Reinforcement learning controls optional search effort after a verified base result; it is neither end-to-end deep RL nor a claim of dominance over always-on Pareto search. \\
Broad baseline and toolchain comparison & Direct \anf{}, ESOP beam/MILP, SSHR, ABC/BDD, ROS-style LUT, mockturtle, Caterpillar API, CirKit, RevKit CLI, and phase/Rz probes. & Tables~\ref{tab:baseline-claim-matrix}, \ref{tab:evidence-matrix}, \ref{tab:paired-statistics}; Fig.~\ref{fig:baselines} & Strong T-count and weighted-score evidence, not universal CNOT/depth/ancilla dominance or full ROS reproduction. \\
High-dimensional and phase-search verification envelope & $n=20$, 24, 28, 32, 40 symbolic term-set checks, $n=48$, 56, 64 ultra-scale symbolic stress, $n=21$--$30$ complete truth-table bridges, Affine-\fprm{} phase search, learned phase shortlist. & Tables~\ref{tab:scale-audit}, \ref{tab:ultra-scale64-stress}, \ref{tab:ultra-scale64-resource-profile}, \ref{tab:validation}, \ref{tab:phase-policy-random}; Fig.~\ref{fig:validation} & Large rows are logically and symbolically verified; complete truth-table enumeration remains limited to bridge slices. \\
\bottomrule
\end{tabularx}
