\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.17\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}p{0.20\linewidth}}
\toprule
Stage & Mechanism & Invariant & Artifact \\
\midrule
Input normalization & Convert a truth table, exported benchmark, or supplied term set into a square-free \anf{} monomial mask set $\mathcal{M}$. & The term set must evaluate to the target Boolean function before any search step is trusted. & \anf{} terms, preset name, and source manifest. \\
Candidate generation & Generate direct \anf{}, \fprm{} polarity, common-factor, Boolean-ring linear-factor, affine, and depth-frontier candidates. & Every action must have an explicit GF(2) expansion back to the original variables. & Candidate logical plans with resource estimates. \\
Search control & Use neural action priors, \mcts{}/beam expansion, staged frontiers, sparse learned gates, and fitted-Q Pareto invocation to allocate the search budget. & Learned decisions rank or skip evaluations; they do not define semantic correctness. & Scored candidate pool and search-time diagnostics. \\
Guarded selection & Compare learned and expensive candidates with deterministic baselines, then apply Pareto filtering before active-score selection. & A selected plan must be a valid generated candidate and remains bounded by the stated guard and score model. & Selected logical plan and non-dominated archive entry. \\
Circuit emission & Expand the selected plan into X/CNOT/\mct{} compute-action-uncompute operations and compute logical resource counts. & The reported score is a ranking objective; T, CNOT, depth, gates, and ancilla are retained separately. & Logical circuit proxy and resource row. \\
Verification and reporting & Check the plan algebraically, check emitted-circuit \anf{} semantics, add full truth-table or phase checks where feasible, and write raw CSV plus manifest rows. & Paper comparisons use matched rows that pass the relevant semantic checks and exclude errors, skips, and timeouts. & \texttt{raw\_*.csv}, \texttt{summary\_*.csv}, \texttt{manifest\_*.json}, and paper tables. \\
\bottomrule
\end{tabularx}
