\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.12\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.28\linewidth}}
\toprule
ROS-facing element & Coverage & Current evidence & Boundary \\
\midrule
ROS literature and task anchor & covered & The manuscript and bibliography cite ROS and frame the current study as logical-layer Boolean-oracle synthesis. & This citation anchor alone does not reproduce the ROS implementation. \\
Official ROS source-discovery and local implementation boundary & not reproduced & The package records that the accessible public artifacts used here are the ROS paper and the STG benchmark table; no official ROS implementation directory is present in the local reproducibility tree. & The current package cannot claim that an official ROS executable or source tree was run. \\
caterpillar/XAG source-family probe & partial & The workstation has a local caterpillar checkout, API/build provenance, and a toy AIG compile/run smoke for logic-network synthesis and SAT/pebbling-related components; no standalone ROS executable is detected in that checkout. & caterpillar availability and the source-only toy smoke are not a full ROS SAT garbage-management reproduction; performance rows are handled only by the separate Caterpillar XAG API probe. \\
Caterpillar XAG API performance probe & partial & The package compiles a local Caterpillar API adapter, converts the 177 traditional n<=6 truth tables to ANF-XAG inputs, runs three XAG strategies, and verifies 531 emitted rows through Caterpillar's circuit-to-logic-network path. & The API rows are ANF-XAG Caterpillar runs, not the official ROS LUT mapper, SAT garbage-management optimizer, reversible-emission flow, or hardware-mapped result. \\
Verified LUT K-sweep proxy & partial & The project runs an ABC if -K sweep for K=3,4,5, verifies each mapped BLIF truth table, and selects the best K per function. & The proxy is not the official ROS mapper or reversible implementation flow. \\
Line and garbage-pressure sensitivity & partial & The line-sensitivity audit reselects the verified LUT sweep under min-ancilla and line-weighted objectives. & This is not SAT garbage management and cannot be called a full ROS reproduction. \\
Executable LUT garbage-management proxy & partial & The project re-runs and truth-table verifies the same best-K LUT DAGs and compares keep-all, fanout-checkpoint, and zero-checkpoint recomputation schedules. & This is still not the official ROS SAT garbage-management algorithm or a reproduced full ROS compiler flow. \\
Executable LUT garbage budget frontier & partial & The budget-frontier audit selects the lowest-score feasible schedule among keep-all, fanout-checkpoint, and zero-checkpoint policies under keep100, line75, line50, line25, and minline peak-ancilla budgets. & This frontier is not an official ROS SAT optimization, reversible-emission, routing, or hardware-mapped result. \\
Exact LUT checkpoint-subset optimizer & partial & The checkpoint optimizer exhaustively enumerates every checkpoint subset for verified LUT DAGs with at most 12 multi-fanout candidates, covering all 177 traditional n<=6 functions and 192 DAGs total. & This exact subproblem is not the full ROS SAT garbage-management algorithm and does not solve the large fanout-heavy DAGs exactly. \\
Published STG optimum-library counterpoint & covered & The project synthesizes the same 54 public truth-table representatives and reports both the negative STG-optimum boundary and the same-slice direct-baseline gains. & This is not a reproduced ROS SAT garbage-management flow and does not replace scalable logical-layer comparisons. \\
Official ROS SAT garbage management & not reproduced & The manuscript, README, and line-sensitivity audit explicitly mark SAT garbage management as not reproduced. & No result may be described as beating or reproducing full ROS with SAT garbage management. \\
Reversible emission and exact-oracle counterpoint & partial & Legacy RevKit CLI probes synthesize exact oracle permutations and serve as a separate reversible-synthesis counterpoint. & The RevKit CLI probe is not the ROS hierarchical LUT plus SAT garbage-management flow. \\
External toolchain availability boundary & covered & Toolchain readiness records ABC, mockturtle, Caterpillar API, CirKit, RevKit API, and legacy RevKit/CirKit availability and separates them from full ROS. & Tool availability is not the same as official ROS reproduction. \\
Claim wording and comparison protocol & covered & Claim matrix, comparison protocol, claim-scope lint, and manuscript limitations state the ROS boundary. & The current evidence cannot support a full-ROS or hardware-mapped dominance statement. \\
Reviewer-facing support visibility & covered & The submission package exposes the ROS-style proxy command and states that full ROS SAT garbage management is not included. & Support-package visibility does not add a new official ROS experiment. \\
\bottomrule
\end{tabularx}
