\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.15\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.27\linewidth}>{\raggedright\arraybackslash}p{0.24\linewidth}}
\toprule
Stage & Operational rule & Source anchors & Reviewer-facing guarantee \\
\midrule
Canonical state & Normalize a truth table, exported benchmark, or supplied term list into a square-free \anf{} monomial set; direct \anf{} remains the fallback plan at every state. & synthesizers.py: anf\_monomials; factor\_plan.py: frozenset, direct\_plan & The search starts from the same Boolean function as the baseline and always has a syntactically valid logical oracle construction. \\
Action generation & Generate monomial factors, linear/Boolean-ring factors, \fprm{} polarity actions, and affine/linear-pair candidates only when they have an explicit GF(2) expansion. & factor\_plan.py: candidate\_actions, linear\_factor\_actions, \_linear\_boolean\_expansion; synthesizers.py: affine\_linear\_pair\_beam\_plan & Learning never invents a semantic rule; it can only rank or select among algebraic actions that the emitter and verifier can expand. \\
Prior-guided tree search & Use the neural scorer to bias action priors, then run PUCT/\mcts{} recursion with greedy rollouts and bounded candidate\_top\_k expansion. & neural\_policy.py: NeuralScorer, score\_many; nmcts\_solver.py: Neural\mcts{}Solver, c\_puct; factor\_plan.py: candidate\_top\_k & The neural component is a budget-allocation prior, not a correctness oracle or an unrestricted circuit generator. \\
Baseline guard & Evaluate deterministic, beam, \mcts{}, neural, and screen candidates as a portfolio; guarded neural variants return the better of the baseline and learned candidate. & synthesizers.py: \_run\_child\_portfolio, min([baseline, neural\_plan], \_portfolio\_result, direct\_anf & A learned or expensive branch is allowed to help but is not allowed to replace a stronger verified deterministic candidate in guarded rows. \\
Pareto archive & Collect candidates from multiple resource profiles, remove candidates dominated in T, CNOT, depth, gates, and peak ancilla, then select by the active score. & synthesizers.py: \_pareto\_front, \_dominates, \_resource\_selection\_key, pareto\_resource\_nmcts & Weighted-score wins are kept separate from multi-resource dominance, which is why tradeoff tables remain part of the Results section. \\
Large-scale controllers & Use depth-frontier policies and sparse gates to decide which high-dimensional Boolean-ring screens to evaluate, with deterministic sparse/full frontiers kept as references. & run\_truth\_bridge\_terms.py: load\_depth2\_guard, load\_frontier\_policy, depth\_frontier\_policy, screen\_depth4 & High-dimensional controllers are planning-time controls over symbolic term-set verification, not hardware schedulers or exhaustive truth-table solvers. \\
Emission and verification & Emit X/CNOT/\mct{} compute-action-uncompute circuits, verify \anf{} semantics symbolically, and use complete truth-table or phase checks where feasible before writing raw result rows. & factor\_plan.py: emit\_plan\_to\_circuit, verify\_plan\_anf, verify\_circuit\_anf, verify\_oracle; run\_experiments.py: correct & Paper comparisons consume matched rows that passed the relevant semantic check; skipped, errored, or timed-out rows are not silently counted. \\
\bottomrule
\end{tabularx}
