\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.16\linewidth}rr>{\raggedright\arraybackslash}X}
\toprule
Evidence family & Rerun tier & Raw files & Raw rows & Dependency boundary \\
\midrule
Lightweight paper-facing rebuild & quick rebuild & 0 & 0 & Python, latexmk, and existing raw artifacts; does not rerun raw sweeps or external probes. \\
Submission metadata closure path & quick metadata audit & 0 & 0 & Does not require private author metadata; filled metadata remains ignored and untracked until author approval. \\
Editorial screening and reviewer-risk support & quick submission-support audit & 0 & 0 & Does not change scientific results; checks public submission-support consistency against existing audit outputs. \\
Cover-letter and venue support packet & quick submission-support audit & 0 & 0 & Does not choose a venue or fill private metadata; checks public upload-support consistency against existing audits. \\
Comparison protocol and claim boundaries & quick comparison audit & 0 & 0 & Quick derived audit; it supports comparison wording but does not rerun raw baseline sweeps. \\
Traditional logical baselines & raw Python rerun & 4 & 4071 & Python rerun; ILP-based subbaselines need Gurobi where enabled. \\
External logical baseline extension & raw Python plus optional solvers & 3 & 2049 & Python with optional Gurobi/logic-tool components; rows with skips/errors remain explicit. \\
ROS-style LUT proxy & raw proxy rerun & 3 & 2472 & Proxy-level LUT analysis only; not a full ROS SAT garbage-management rerun. \\
ROS reproduction boundary audit & quick audit & 3 & 2472 & Checks scope and evidence boundaries; it deliberately records that full official ROS is not reproduced. \\
mockturtle KLUT-to-XAG probe & external toolchain rerun & 2 & 241 & Requires the recorded mockturtle checkout/header path; still a logical proxy, not reversible mapping. \\
CirKit AIG/MC probe & external toolchain rerun & 2 & 241 & Requires the recorded CirKit executable/commit; results are logical estimates, not hardware mapping. \\
RevKit exact and Rz probes & external toolchain rerun & 5 & 3194 & Requires RevKit CLI/API availability; Rz rows are phase/sensitivity probes, not final Clifford+T decomposition. \\
Phase and affine FPRM branch & raw phase rerun and training & 7 & 11859 & Logical phase verification up to global phase; not approximate rotation synthesis. \\
Learned-control and ablations & training plus ablation rerun & 13 & 3959 & Training can use MPS/GPU when available; learned controls rank, gate, or allocate search only. \\
High-dimensional symbolic screen-scale runs & large raw rerun & 76 & 11480 & Symbolic or generated-instance verification; not exhaustive truth-table enumeration for all large n. \\
External high-dimensional resource extensions & large raw rerun & 4 & 528 & Generated large-instance comparisons; external availability and timeout behavior are recorded in manifests. \\
Boolean screen, frontier, and gate auxiliaries & training plus ablation rerun & 11 & 2170 & Auxiliary policy-selection evidence; not all rows are promoted as final-quality gains. \\
Exact, resource-sweep, and development probes & auxiliary raw rerun & 11 & 12524 & Development and auxiliary evidence retained in the payload; not all rows correspond to headline manuscript claims. \\
Complete truth-table bridge slices & bridge raw rerun & 8 & 580 & Narrow bridge slices because full truth tables grow exponentially. \\
\bottomrule
\end{tabularx}
