\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.21\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.21\linewidth}>{\raggedright\arraybackslash}p{0.19\linewidth}}
\toprule
Role & Compared methods & Why it matters & Supported claim & Excluded claim \\
\midrule
Primary resource-efficiency baselines & Direct \anf{}, AND-direct \anf{}, ESOP beam/MILP, BDD/ABC-ESOP, SSHR-H/SSHR-I & These methods solve the same bit-flip Boolean-oracle task under the paper's logical resource model. & \method{} improves T-count and weighted score on matched small functions while SSHR remains a strong CNOT counterpoint. & Does not prove universal CNOT, depth, ancilla, or hardware-level optimality. \\
External logic-network probes & ABC AIG/XAG/LUT, ROS-style LUT and garbage-budget proxy, mockturtle KLUT-to-XAG, CirKit AIG/MC & They test whether mature Boolean-network optimization already removes the apparent advantage over direct algebraic baselines. & The score advantage persists against stronger exported-network and official-header tool probes. & Does not reproduce full ROS SAT garbage management or reversible/hardware mapping. \\
Exact reversible-synthesis probe & Legacy RevKit CLI TBS/DBS/RMS exact-oracle portfolio & It embeds each function as $(x,y)\mapsto(x,y\oplus f(x))$ and checks a genuine reversible-synthesis toolchain. & \method{} has lower T-count and weighted score against this portfolio but pays more auxiliary lines. & Does not imply lower line count, routed depth, or mapped Clifford+T cost. \\
Phase/\rz{} branch & RevKit oracle\_synth, phase-parity \anf{}, fixed-polarity \fprm{}, affine \fprm{}, learned phase shortlist & It tests whether the same search framing extends to phase-oracle and affine-preconditioned \rz{} cost proxies. & Affine and learned candidate pruning improve verified logical phase/\rz{} proxy objectives. & Not a final Clifford+T decomposition; only a coarse sequence-smoke audit emits bounded single-qubit strings. \\
Internal search ablations & No-\mcts{} portfolio, learned prior off, guard off, Pareto archive off, depth-frontier variants, sparse gate & They separate representation effects from the contribution of search, neural ranking, guards, and budget control. & AI-guided search and guards add measurable gains or time savings beyond deterministic construction. & Does not support a claim that deep reinforcement learning alone causes the whole improvement. \\
Scaling and correctness bridges & $n=20$, 24, 28, 32, 40 term-set symbolic runs; $n=48$, 56, 64 ultra-scale symbolic stress; $n=21$--$25$ complete truth-table bridge rows & They push semantic checks beyond the small truth-table slice while keeping full verification where still feasible. & The emitted logical-layer circuits remain symbolically and bridge-truth-table verified at larger dimensions. & Does not make exhaustive high-dimensional truth-table benchmarking feasible or complete. \\
Trade-off audits & Raw multi-resource dominance, line-aware LUT reselection, schedule proxy, sparse-threshold sweep & They prevent a weighted-score result from hiding CNOT, depth, line-count, or planning-time tradeoffs. & The method occupies a strong T/score point with explicit depth, CNOT, ancilla, and runtime boundaries. & Does not justify reporting a single-metric victory as complete dominance. \\
\bottomrule
\end{tabularx}
