\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.17\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.18\linewidth}}
\toprule
Question & Target & Evidence & Quantitative answer & Boundary \\
\midrule
Are gains only over weak algebraic baselines? & Direct \anf{}, ESOP beam/MILP, ABC/BDD exports & Internal logical baselines: 1770/1770; Exported SSHR/ABC/BDD extension: 1416/1416 & Pareto vs direct \anf{} 172/1/4, -67.80\%; vs ESOP-MILP 167/3/7, -29.84\%; vs ABC-XAG 177/0/0, -65.58\% & No universal CNOT, depth, ancilla, line-count, or hardware-mapped optimality claim. \\
Is SSHR the whole comparison target? & SSHR-H and SSHR-I CNOT & Internal logical baselines: 1770/1770; Exported SSHR/ABC/BDD extension: 1416/1416 & Pareto vs SSHR-H 173/4/0, -41.06\%; vs SSHR-I CNOT 173/4/0, -31.89\%; SSHR-H four-resource dominance 33/4/140/0 & Do not claim CNOT dominance over SSHR; SSHR remains a real CNOT counterpoint. \\
Does the advantage survive external logic synthesis? & ROS-style LUT, mockturtle XAG, CirKit AIG/MC & ROS-style LUT proxy: 309/309 best rows; 927/927 K-sweep rows; 927/927 garbage-proxy rows; mockturtle KLUT-to-XAG probe: 241/241; CirKit AIG/MC probe: 241/241 & ROS best-K 309/0/0, -84.27\%; mockturtle n$\leq$6 166/11/0, -31.50\%; CirKit n$\leq$6 177/0/0, -62.34\% & Not a full ROS SAT garbage-management, reversible-emission, routing, or hardware-mapped comparison. \\
Does it beat published tiny-function optima? & Published STG n=4/5 optimum table & Published STG optimum-library counterpoint: 270/270 & Pareto vs STG T-count optimum 0/40/14, +84.26\%; vs direct \anf{} on STG slice 50/4/0, -58.10\% & No claim of beating published STG T-count, T-depth, or qubit optima on n=4/5 spectral representatives. \\
What does RevKit test? & Legacy RevKit exact oracle and RevKit phase/\rz{} branch & Legacy RevKit CLI exact oracle: 708/708; RevKit phase/\rz{} branch: 531/531; Learned phase pruning: 7611/7611 & RevKit CLI exact oracle 173/0/4, -67.28\%; Affine phase vs RevKit oracle\_synth 177/0/0, -65.50\% & Not lower auxiliary-line count, routed depth, or final approximate-rotation Clifford+T synthesis. \\
What part is actually AI/\mcts{}? & No-\mcts{} portfolio, Pareto archive, learned/random controls & Search-control audit: 10/10 pass & Resource over no-\mcts{} 54/0/123, -1.44\%; Pareto over no-\mcts{} 106/0/71, -4.69\%; learned vs random prior 17/8/152, -0.15\% & Do not state that deep reinforcement learning alone explains the full resource reduction. \\
Is the evidence only small-scale? & $n=20$--64 symbolic runs and $n=21$--25 complete truth-table bridges & High-dimensional frontier search: 2088/2088; Complete truth-table bridges: 400/400 & Stage-gated vs all-depth scale 0/4/92, +0.04\% score; -25.43\% time; ultra n=48,56,64 stress 480/480 plan+circuit verified; Bridge rows verify plan, emitted symbolic circuit, and complete truth table for $n=21$-25. & Not exhaustive high-dimensional truth-table benchmarking or global optimality proof. \\
Does weighted score hide bad tradeoffs? & Four-resource dominance and non-dominated method pool & 12-method n$\leq$6 dominance pool; 177 matched functions & Pareto-\method{} is 170/177 non-dominated; RevKit CLI exact oracle four-resource dominance 3/0/170/4; CirKit AIG/MC four-resource dominance 21/0/156/0 & Do not turn weighted-score wins into a complete Pareto or hardware-dominance claim. \\
\bottomrule
\end{tabularx}
