\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.11\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.25\linewidth}}
\toprule
Screening item & Status & Supported decision & Boundary \\
\midrule
Logical-layer scope visible at first screening & pass & The manuscript can be sent to reviewers as a logical-layer oracle-synthesis paper. & Do not imply hardware routing, native-gate scheduling, noise modeling, or device execution. \\
Novelty and comparison route visible & pass & The screening package explains why SSHR is a baseline and why comparisons are layered. & The claim is not universal superiority over every synthesis method. \\
Comparison target roles visible & pass & The package makes comparison roles explicit before the results are read as a universal leaderboard. & Role labels clarify the current evidence; they do not broaden any comparison beyond the logical-layer claim. \\
Counterpoint and negative-result visibility & pass & Unfavorable metric evidence is visible before review rather than hidden in raw tables. & Weighted-score wins must stay separated from raw resource dominance. \\
AI and MCTS contribution bounded & pass & The manuscript can claim neural/MCTS search-control support without overclaiming deep RL. & The largest gains remain tied to algebraic action space and guarded/Pareto selection. \\
Large-scale verification boundary visible & pass & Large-scale evidence is framed as symbolic verification plus bounded truth-table bridges. & Do not claim exhaustive high-dimensional truth-table benchmarking. \\
Reproducibility path visible & pass & The submission package exposes a clear reviewer path from claims to files and scripts. & The lightweight rebuild verifies paper-facing outputs; raw sweeps remain heavier rerun tiers. \\
Author and venue gate explicit & pass & The remaining nontechnical submission gate is explicit and private rather than implicit. & Author order, affiliations, funding, conflicts, venue choice, and archive links still require author input. \\
Editorial reading path present & pass & The support package gives editors a concise route to judge fit before full review. & This is a navigation aid, not an acceptance guarantee. \\
\bottomrule
\end{tabularx}
