\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.15\linewidth}>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.08\linewidth}>{\raggedleft\arraybackslash}p{0.07\linewidth}>{\raggedleft\arraybackslash}p{0.08\linewidth}>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}X}
\toprule
Level & Evidence role & Scope & Items & Checked & Verification strength & Claim use / boundary \\
\midrule
1. Exact same-task core & Headline bit-flip oracle comparison & $n=3$--$6$ & 177 & 3819 & complete truth-table checks & Primary paired T-count and weighted-score claim over same-function baselines. Boundary: Small n is fair and exact, but not a large-n optimality certificate. \\
2. Small optimum counterpoint & Negative control against precomputed public optima & $n=4$--$5$ & 54 & 270 & public truth tables with exact small-function checks & Shows that the paper does not hide stronger tiny-function optimum rows. Boundary: Counterpoint evidence only; it is not a headline victory over optimum libraries. \\
3. External toolchain stress & Independent Boolean-network and LUT/XAG/AIG pressure & $n=3$--$18$ & 373 & 968 & export/readback and logic-network checks & Checks that the resource story is not only against local hand-written baselines. Boundary: Proxy logical-tool evidence, not a full reversible or hardware-mapped reproduction. \\
4. Reversible and phase boundary & Exact reversible and phase/\rz{} transfer counterpoint & $n=3$--$6$ & 181 & 10109 & permutation checks, phase checks up to global phase, smoke sequence checks & Separates reversible/phase transfer evidence from the main bit-flip result. Boundary: Not a final approximate Clifford+T rotation-synthesis comparison. \\
5. Complete high-n semantic bridge & Large-n semantic bridge & $n=21$--$30$ & 60 & 880 & complete truth-table construction and emitted-circuit checks & Connects symbolic large-instance plans to exact semantic checks up to n=30 generated functions. Boundary: Deliberately narrow because full truth tables grow exponentially. \\
6. Ultra-scale symbolic stress & Scalability and resource-profile stress test & $n=20$--$64$ & 384 & 7392 & symbolic \anf{} and emitted-circuit \anf{} checks & Shows the bounded search and emitter still run on generated $n=20$--$64$ logical instances. Boundary: Symbolic verification is not exhaustive high-dimensional truth-table enumeration. \\
7. AI/search-control attribution & Neural/\mcts{} causal and stability evidence & $n=3$--$40$ & 225 & 15930 & same-budget controls, held-out splits, independent seeds, semantic checks & Separates learned ranking, frontier policies, guards, and \mcts{} controls from representation effects. Boundary: Does not claim deep learning alone causes the full resource reduction. \\
8. Manuscript integration & Experimental-strength ladder is visible in all submission variants & not applicable & 0 & 0 & source anchor check & Places benchmark scale, semantic strength, and boundaries before result tables. Boundary: Integration evidence is not a new experiment. \\
\bottomrule
\end{tabularx}
