\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.16\linewidth}>{\raggedright\arraybackslash}p{0.10\linewidth}r>{\raggedleft\arraybackslash}p{0.21\linewidth}>{\raggedleft\arraybackslash}p{0.21\linewidth}>{\raggedright\arraybackslash}X}
\toprule
Component & Class & Pairs & Score $\Delta$ [95\% CI] & Effort $\Delta$ [95\% CI] & Interpretation \\
\midrule
Depth-frontier policy & promoted & 48 & $+0.04\%$ [$+0.00$, $+0.09$] & planning time: $-51.30\%$ [$-56.82$, $-45.67$] & Preserves oracle-frontier score within a narrow interval while reducing all-depth evaluation effort. \\
Stage-gated frontier & promoted & 96 & $+0.04\%$ [$+0.00$, $+0.09$] & planning time: $-25.43\%$ [$-30.80$, $-20.15$] & Validation-calibrated gate keeps score near the all-depth frontier while reducing planning time. \\
Sparse depth-4 gate & promoted & 144 & $+0.00\%$ [$+0.00$, $+0.00$] & evaluation time: $-13.43\%$ [$-17.20$, $-9.86$] & Seed-stable skip gate preserves sparse-frontier score and reduces sparse-frontier evaluation time. \\
Rank-diverse phase shortlist & promoted & 38 & $-2.48\%$ [$-5.21$, $-0.26$] & exact forms: $-93.75\%$ [$-93.75$, $-93.75$] & Policy shortlist improves the small-budget score while using far fewer exact evaluations than wide128. \\
Bit-flip learned prior & limited & 177 & $-0.15\%$ [$-0.30$, $-0.03$] & runtime: $+48.05\%$ [$+30.91$, $+68.18$] & Score effect is small and runtime-positive, so this remains a limited quality signal, not a speed claim. \\
Bit-flip low-budget prior & bounded & 1062 & $-1.04\%$ [$-1.25$, $-0.84$] & runtime: $+24.22\%$ [$+21.90$, $+26.72$] & Low-budget learned prior has a bounded quality effect with visible runtime cost. \\
Boolean neural guard & limited & 24 & $-0.12\%$ [$-0.27$, $-0.00$] & runtime: $+94.49\%$ [$+81.75$, $+106.10$] & Quality effect is small and runtime-positive, so this remains a limited guard diagnostic. \\
Root-action neural candidate extension & bounded & 33 & $-0.08\%$ [$-0.16$, $-0.02$] & -- & Root-only candidate extension is bounded score evidence; runtime is not claimed. \\
\bottomrule
\end{tabularx}
