\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.24\linewidth}}
\toprule
Claim anchor & Evidence gate & Allowed interpretation & Excluded interpretation \\
\midrule
Neural component in the title & learned-control rows=9, promoted=4, bounded=3, limited=2, not\_promoted=0 & Neural policies and learned gates are bounded ranking, pruning, or budget-allocation controls with promoted and limited evidence classes. & Do not claim that deep learning alone explains the resource reduction. \\
\mcts{} component in the title & search-control rows=11, needs\_revision=0 & \mcts{} and Pareto search add measured, non-degrading increments over strengthened deterministic portfolios. & Do not attribute the full improvement to \mcts{} alone. \\
Causal search-control isolation & bit-flip random rows=18, budget-sweep raw rows=2124, frontier random rows=3 & Same-budget, low-budget, and same-candidate controls support ranking and budget-allocation claims. & Do not use random-control rows as speed, hardware-scheduling, or deep-RL-only evidence. \\
Resource-constrained objective & schedule-proxy rows=8, needs\_revision=0 & The score and schedule-proxy evidence support resource-constrained logical-layer optimization with visible tradeoffs. & Do not turn weighted-score wins into all-resource or hardware-mapped dominance. \\
Verified workflow rather than learned correctness & algorithm rows=7, budget rows=8 & Learning controls action order, pruning, or budget; correctness comes from GF(2), emitted-circuit, truth-table, and phase verifiers. & Do not imply that a neural model certifies circuit semantics. \\
Large-scale claim boundary & ultra stress rows=11, profile rows=20 & Large instances are supported by symbolic term-set/emitted-circuit checks and smaller complete truth-table bridge slices. & Do not claim exhaustive truth-table benchmarking or optimality for all large $n$. \\
Logical-layer boundary & claim-scope unresolved=0, threat rows=7 & The paper is a logical-layer synthesis study. & Do not claim routing, native-gate scheduling, noise, or magic-state-factory resources. \\
\bottomrule
\end{tabularx}
