\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.17\linewidth}>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.23\linewidth}>{\raggedright\arraybackslash}p{0.20\linewidth}}
\toprule
Line of work & Representative work & Main lever & Gap for this paper & Manuscript use \\
\midrule
BDD-based reversible synthesis & BDD reversible synthesis~\cite{wille2009bdd} & Symbolic decision-diagram representation for large Boolean functions. & Representation scalability does not by itself optimize T, CNOT, depth, gates, and ancilla jointly. & Used as a representation-level baseline family, not as the proposed search space. \\
LUT/ROS-style oracle synthesis & ROS and back-end-aware oracle synthesis~\cite{meuli2020ros,yu2025backend} & Resource-aware LUT mapping and downstream implementation-cost estimates. & Full ROS garbage-management and hardware/back-end mapping are outside the logical-layer claim. & Reproduced through a verified ROS-style LUT proxy and line-aware reselection stress tests. \\
XAG and multiplicative complexity & XAG compilation and multiplicative-complexity oracle cost~\cite{meuli2019multiplicative,meuli2022xag} & Separates XOR-linear structure from AND nodes as a non-Clifford proxy. & A fixed network optimization flow may miss algebraic \fprm{}/\anf{} search actions and Pareto tradeoffs. & Used through ABC, mockturtle, and CirKit probes plus exact small XAG lower-bound checks. \\
Logic and reversible toolchains & ABC, EPFL libraries, RevKit, mockturtle, and CirKit~\cite{brayton2010abc,soeken2018epfl,soeken2012revkit,revkit,mockturtle,cirkit} & Mature optimization passes and reversible-synthesis flows. & Tool output defines strong baselines but does not expose the neural/\mcts{} algebraic action policy. & Used as external probes and exact-oracle reversible-synthesis comparisons. \\
SSHR geometric synthesis & Parallelotope-based CNOT-oriented synthesis~\cite{zheng2025sshr} & Small-scale Boolean hypercube geometry targeting CNOT-oriented covers. & The objective is CNOT-oriented and small-function focused, not a general resource-weighted AI search. & Used as a CNOT-oriented small-function baseline; not used by the proposed method. \\
Learning-guided circuit synthesis & AlphaZero, reinforcement learning, MCTS, and ZX-guided synthesis~\cite{tsaras2024shortcircuit,rietsch2024unitary,kremer2025nonclifford,riu2025rlzx,zhou2022qctmcts,machiya2026monteq} & Learns or searches over circuit-design and circuit-transformation actions. & Most targets are classical circuits, unitary synthesis, routing/transformation, ZX rewriting, or Hamiltonian simulation rather than Boolean-oracle \anf{}/\fprm{} term search. & Motivates neural/\mcts{} control while keeping actions verifiable at the Boolean-algebraic oracle layer. \\
\bottomrule
\end{tabularx}
