\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.13\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.25\linewidth}}
\toprule
SSHR-facing element & Scope & Current evidence & Boundary \\
\midrule
SSHR literature and method boundary & covered & The manuscript cites SSHR, states that the proposed method does not search parallelotope candidates, and uses SSHR as a CNOT-oriented small-function baseline. & The proposed method is not an SSHR variant and does not inherit SSHR's CNOT-only objective. \\
SSHR Table VIII candidate-space anchor & source-anchored & The development repository contains the SSHR candidate-count reference and table runner when the full source tree is present; the upload payload records the boundary without requiring that parent source tree. & This audit does not rerun every published SSHR random benchmark table inside the lightweight submission rebuild. \\
SSHR-H same-task baseline rows & covered & The traditional bit-flip benchmark includes 177 correct SSHR-H rows and the manuscript keeps SSHR-H visible as the best mean-CNOT baseline in the traditional table. & The SSHR-H row is not evidence of CNOT-only dominance by the proposed method. \\
SSHR-I CNOT/T extension rows & partial & The external n<=6 extension includes SSHR-I CNOT-objective and T-objective rows for the same 177 functions with correctness checks and explicit timeout metadata. & The n<=6 extension is not an exact certificate for all SSHR-I random-paper settings. \\
n<=4 exact/pilot SSHR-I cross-check & covered & The n<=4 external pilot records 72 functions and 216 SSHR-H/SSHR-I rows, and exact small-slice analyses include SSHR-I references as counterpoints. & Even this slice is a counterpoint under the paper's logical resource projection, not a proof of global reversible optimality. \\
SSHR tradeoff in resource-weight sensitivity & covered & The resource-weight audit explicitly keeps SSHR-H and SSHR-I CNOT-only losses visible while showing paper-score and T-score advantages. & Weighted-score wins cannot be rewritten as all-metric or CNOT-only SSHR dominance. \\
Comparison and claim-boundary integration & covered & Comparison answer, target-validity, threats-to-validity, and claim-scope gates all mark SSHR as a CNOT counterpoint rather than the whole comparison target. & No paper-facing text may claim full SSHR replacement, universal optimality, or hardware-mapped dominance. \\
Reviewer payload visibility & covered & The submission package exposes the comparison role, reviewer concern brief, and artifact guide so a reviewer can locate SSHR rows and their boundary quickly. & Support-package visibility does not add a new SSHR random-table rerun. \\
\bottomrule
\end{tabularx}
