\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.22\linewidth}rr>{\raggedright\arraybackslash}p{0.14\linewidth}>{\raggedright\arraybackslash}X}
\toprule
Payload group & Files & Missing & Digest & Boundary \\
\midrule
Manuscript source & 5 & 0 & \texttt{c035a1170aa3} & Compiled PDF is checked by readiness audit to avoid self-referential hashes. \\
Paper tables & 211 & 0 & \texttt{6fc53684d293} & Terminal submission audit tables are excluded from the stable payload digest. \\
Submission figures & 28 & 0 & \texttt{63937fb65f1e} & Includes generated figure assets and plotted source data, not raw benchmark reruns. \\
Raw measurements & 166 & 0 & \texttt{168b6e797fdd} & Raw CSVs are regenerated only by the heavier run scripts, not by the lightweight rebuild. \\
Derived summaries & 477 & 0 & \texttt{f3556750e2a5} & Terminal submission/package outputs are excluded so this manifest remains stable. \\
Run manifests & 148 & 0 & \texttt{7e24db1c7f98} & Submission-level terminal manifests are excluded from this digest group. \\
Scripts and docs & 178 & 0 & \texttt{1f0efb4c61b0} & Includes reproducible entry points and top-level core implementation modules; raw sweeps still require their individual drivers. \\
Models & 21 & 0 & \texttt{1b2a25f8280f} & Includes trained local policy artifacts when present; model retraining is not part of the lightweight rebuild. \\
External adapters & 1 & 0 & \texttt{de5aa3b78998} & Includes local adapter source files used for external toolchain probes, not vendored tool repositories. \\
Submission support & 18 & 0 & \texttt{89975da3fdb6} & Includes public package README, author-input packet, artifact guide, cover-letter, declaration, checklist, reviewer-brief, editor-screening, venue-selection, and structured metadata templates; ignored generated private submission text is excluded. \\
\bottomrule
\end{tabularx}
