\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.22\linewidth}>{\raggedright\arraybackslash}p{0.11\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.25\linewidth}}
\toprule
Support-packet item & Status & Supported use & Boundary \\
\midrule
Cover letter preserves logical-layer scope & pass & The cover letter can introduce the manuscript without overclaiming hardware mapping or physical execution. & The cover letter still needs author, editor, reviewer, and prior-dissemination fields before upload. \\
Cover letter exposes the comparison envelope & pass & The cover letter summarizes layered baselines and directs editors to the comparison evidence. & It should not be read as universal dominance over every synthesis or compilation method. \\
Novelty/comparison scorecard is visible & pass & The support packet gives editors and reviewers a compact route from comparison questions to evidence and limitations. & The scorecard indexes existing evidence; it does not add a new metric or broaden the logical-layer claim. \\
Comparison target validity audit is visible & pass & The support packet gives reviewers a direct route from comparison targets to role labels and excluded claims. & The validity audit classifies existing comparisons; it does not convert secondary probes into full hardware-mapped baselines. \\
Chinese comparison handoff is visible & pass & The author-facing Chinese handoff keeps comparison, novelty, and excluded-claim language aligned before upload or reviewer response. & It is a navigation and wording guide over existing evidence; it does not add experiments or replace author/venue metadata. \\
Author declarations keep private fields explicit & pass & The declarations packet is a structured intake path rather than a hidden or implicit author task. & Final authorship, funding, conflicts, archive links, and AI disclosure remain human-gated. \\
Venue policy gate is visible before upload & pass & The venue-choice step is concrete enough for the author to fill the private metadata file. & The audit does not choose the journal; it only checks that the choice is explicit and policy-gated. \\
Private preview path remains safe & pass & Authors can generate private submission-system text after filling metadata without committing it. & Tracked audit outputs remain public and redacted; private generated Markdown files stay ignored. \\
Anonymous-review fork is not conflated with author version & pass & The support packet separates the current author-labeled manuscript from the venue-dependent anonymous path. & Anonymous-review policy and anonymous archive links still require target-venue input. \\
Editor and reviewer triage is aligned & pass & The editor-facing and reviewer-facing triage path points to the same bounded evidence package. & Triage briefs are navigation aids, not acceptance guarantees. \\
Upload checklist cites terminal verifiers & pass & The public handoff points authors to the same terminal checks used by the repository. & The checklist cannot replace final venue-system proof review. \\
\bottomrule
\end{tabularx}
