\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.29\linewidth}>{\raggedright\arraybackslash}p{0.19\linewidth}>{\raggedright\arraybackslash}X}
\toprule
Claim family & Paper-facing use & Manuscript anchor & Boundary \\
\midrule
Method formulation & Defines Resource-NMCTS as a source-anchored logical ANF/FPRM search workflow. & Method, Tables method-workflow, algorithm-contract, and search-budget-contract & Establishes executable stages, semantic/resource guarantees, and bounded search budgets, not a hardware compiler or global optimality proof. \\
Contribution mapping & Links each stated contribution to implementation, evidence, and claim boundary. & Introduction, Table contribution-map & Prevents the introduction from making unsupported novelty claims. \\
Novelty and comparison scorecard & Answers reviewer-facing questions about method identity, comparison meaning, external probes, tradeoffs, AI isolation, and scale boundary. & Introduction, Table novelty-comparison-scorecard & Provides a reviewer-facing index over existing evidence; it does not add a new metric or broaden the logical-layer scope. \\
Primary small-function resources & Supports T-count and weighted-score claims on matched n$\leq$6 functions. & Results, traditional functions & Same logical cost model; not a CNOT-only or hardware-level claim. \\
Baseline scope and fairness & Explains why each baseline family is comparable and which claim it can support. & Experimental Design, baseline matrices, target-validity table, and counterpoint audit & Treats comparisons as layered evidence with explicit roles and reports unfavorable metric counterpoints rather than a universal leaderboard. \\
External toolchain probes & Traces ROS-style LUT, mockturtle, CirKit, and RevKit CLI comparison evidence. & Results, external probes & Logic-level probes or exact-oracle reversible probe; not full hardware mapping. \\
Multi-resource tradeoff & Audits whether weighted-score wins imply raw-resource, schedule-proxy, or auxiliary-lifetime dominance. & Results, raw multi-resource dominance and schedule-proxy audit & Dominance uses logical T-count, CNOT, depth, peak ancilla, T-depth proxy, and auxiliary lifetime; no routing or native-gate scheduling is claimed. \\
Learned-control contribution & Separates search-control baselines and promoted learned controllers from limited diagnostics. & Results, search contribution and ablation & Supports guarded learned-control evidence, not a claim that RL alone explains all gains. \\
High-dimensional verification & Traces large symbolic checks through n=64, phase checks, and complete truth-table bridge slices. & Results, high-dimensional verification & Large rows are symbolic or bridge-slice verified, not exhaustive high-dimensional truth tables. \\
Archive package integrity & Hashes stable submission payload groups and records archive boundaries. & Experimental Design, archive manifest & Excludes terminal submission audits and compiled PDF from payload hashes to avoid self-reference. \\
Submission support and venue gate & Traces target-venue decision support, support-packet consistency, and author-gated submission metadata. & Submission package, target venue brief and author-input packet & Supports a source-backed venue decision path; final venue, declarations, archive links, and anonymous-review status remain author input. \\
Reproducibility package & Documents compute envelope, worker manifests, artifact counts, raw rerun entry points, and availability section. & Experimental Design and Data and Code Availability & Repository-relative package until an archival DOI or anonymous link is supplied. \\
\bottomrule
\end{tabularx}
