\begin{tabularx}{\linewidth}{r>{\raggedright\arraybackslash}p{0.20\linewidth}>{\raggedright\arraybackslash}p{0.13\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.23\linewidth}}
\toprule
Order & Venue & Fit & Pre-upload action & Boundary \\
\midrule
1 & ACM TQC & strong & Use ACM's current primary article template in single-column review format, add ACM journal metadata/keywords if required, and keep artifact links ready. & Confirm ACM primary-article template version, approved LaTeX packages, article type, references, artifact policy, and any author/AI disclosure requirements. Source: https://www.acm.org/publications/authors/submissions \\
2 & Quantum & strong & Post or cross-list the preprint to quant-ph, sharpen the first-pages contribution summary, and prepare mandatory author-contribution plus AI-use statements. & Confirm arXiv/quant-ph submission route, author contribution statement, AI-use disclosure, and optional template expectations. Source: https://quantum-journal.org/instructions/authors/ \\
3 & IEEE TQE & moderate-to-strong & Convert to IEEE style, confirm the open-access APC/funding path, and keep the logical-layer software-engineering boundary explicit. & Confirm IEEE template, article type, open-access/APC path, reference style, and disclosure requirements. Source: https://tqe.ieee.org/submission-process/ \\
4 & IEEE TCAD & moderate & Condense to TCAD page limits and emphasize synthesis algorithms, verification, tool reproducibility, and EDA relevance. & Confirm IEEE two-column format, regular-paper page limit, abstract length, index terms, keywords, and reference style. Source: https://ieee-ceda.org/publications/tcad/tcad-paper-submissions \\
5 & QST & selective/high-risk & Strengthen the broad-impact motivation, choose Paper versus Letter only after checking article-type expectations, and align declarations with IOP requirements. & Confirm article type, TeX/LaTeX submission route, peer-review model, author contribution/funding/conflict fields, and supplementary data policy. Source: https://publishingsupport.iopscience.iop.org/journals/quantum-science-technology/ \\
\bottomrule
\end{tabularx}
