\begin{tabularx}{\linewidth}{>{\raggedright\arraybackslash}p{0.18\linewidth}>{\raggedright\arraybackslash}p{0.25\linewidth}>{\raggedright\arraybackslash}X>{\raggedright\arraybackslash}p{0.22\linewidth}}
\toprule
Threat & Risk & Mitigation evidence & Residual boundary \\
\midrule
Logical-layer abstraction & Readers may infer hardware routing, native-gate, noise, or magic-state-factory resource claims. & The abstract, discussion, claim-scope lint, and payload README state that the paper reports logical-layer resources only. & No placement, routing, native-gate scheduling, noise, or factory-level accounting is evaluated. \\
Weighted-score aggregation & A single score could hide unfavorable CNOT, depth, ancilla, or lifetime behavior. & Raw dominance, schedule-proxy, weight-robustness, and counterpoint audits expose resource dimensions separately from the weighted score. & The method is presented as a strong T-count and weighted-score point, not complete raw-resource dominance. \\
Baseline comparability & External logic-network, reversible, phase, and ROS-style rows could be mistaken for one fully uniform compiler benchmark. & The comparison matrices assign each baseline family a role, verified evidence, usable claim, and excluded claim. & ROS-style and logic-network probes remain logical proxies; RevKit rows are exact-oracle or phase proxies, not mapped circuits. \\
AI/\mcts{} attribution & The manuscript could overstate deep learning or \mcts{} as the sole reason for the gains. & Search-control, random-prior, random-depth, and learned-control audits separate algebraic search space, \mcts{}, Pareto archives, and learned ranking. & Learned controls are bounded and sometimes runtime-negative; they are not promoted as the whole resource-reduction mechanism. \\
High-dimensional verification envelope & Large-n symbolic rows may be read as exhaustive truth-table benchmarking or optimality evidence. & Scaling, ultra-scale, resource-profile, and truth-bridge audits separate symbolic verification from complete truth-table checks. & Complete truth-table verification is limited to generated bridge slices; $n=26$--$64$ rows are not exhaustive truth-table enumerations. \\
Statistical and benchmark representativeness & Mean improvements could be driven by outliers or by an unrepresentative benchmark subset. & Paired statistics, bootstrap intervals, and headline consistency checks recompute matched comparisons from CSV evidence. & The evidence covers the generated and benchmarked slices in the artifact package, not all Boolean functions. \\
Reproducibility and package drift & A complete-looking manuscript could drift from the scripts, raw rows, tables, and archive manifest. & Reproducibility, artifact-registry, and archive-manifest audits connect scripts, raw rows, summaries, tables, and manuscript payload groups. & The lightweight rebuild regenerates paper-facing artifacts but does not rerun heavy raw sweeps or neural training jobs. \\
\bottomrule
\end{tabularx}
