\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{microtype}

\newcommand{\method}{Resource-NMCTS}
\newcommand{\affinemethod}{Affine-NMCTS}
\newcommand{\profilemethod}{Profile-Resource-NMCTS}
\newcommand{\paretomethod}{Pareto-Resource-NMCTS}
\newcommand{\dataset}{evidence\_affine}
\newcommand{\ablationdataset}{ablation\_affine}
\newcommand{\traditionaldataset}{traditional\_resource}
\newcommand{\largedataset}{large\_resource\_core}
\newcommand{\highdimdataset}{highdim\_resource}
\newcommand{\scaledataset}{highdim\_scale\_resource}
\newcommand{\ultradataset}{ultra\_highdim\_resource}
\newcommand{\megadataset}{mega\_highdim\_resource}

\title{Resource-NMCTS: Neural Monte Carlo Tree Search with Affine Boolean Preconditioning for Resource-Constrained Quantum Oracle Synthesis}
\author{Zixiang Zhou}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Quantum Boolean oracle synthesis is a central subroutine in many quantum
algorithms, yet direct algebraic-normal-form constructions can be expensive in
T-count, depth, and ancillary workspace.  We study oracle synthesis as a
logic-level search problem over compute/uncompute factorizations of Boolean
monomials.  The core \affinemethod{} solver combines resource-weighted neural
Monte Carlo tree search with affine Boolean input preconditioning, allowing the
search to change the XOR coordinate system before factoring the resulting
fixed-polarity Reed--Muller representation.  The full \method{} method adds a
budgeted resource-adaptive portfolio guard that selects, under the current
weighted objective, among direct ANF, FPRM/affine neural MCTS, and tractable
fixed-coordinate MCTS or ESOP cube-beam candidates; it does not use SSHR
candidates.  On the current
\dataset{} benchmark of 322 Boolean functions, \affinemethod{} is correct on
all functions and reduces mean T-count by 61.83\% relative to direct ANF
synthesis.  On a separate $n\leq 6$ traditional-baseline slice, the
\paretomethod{} archive has the lowest mean T-count and weighted score, and
improves on \method{} with 74 score wins, no losses, and 103 ties.  It has
174 score wins and no losses against ESOP cube beam search, and 167 score
wins, 3 losses, and 7 ties against time-limited weighted ESOP MILP; aggregated
by variable count, it reduces total T-count and CNOT count versus ESOP-MILP in
every $n=3,\ldots,6$ group and lowers aggregate peak ancilla for all groups
except the tied $n=3$ case.  Against the exported ABC-ESOP baseline on the
same 177 functions, it reduces aggregate T-count by 25.18\%, CNOT count by
4.38\%, peak ancilla by 14.04\%, and weighted score by 23.00\%, with 170 score
wins, 1 loss, and 6 ties.  On an
exported external comparison, \method{} has 69 score wins and 3 losses against
the exact $n\leq 4$ CNOT-optimized SSHR-I pilot, 168 score wins and 9
losses against the time-limited $n\leq 6$ SSHR-I extension, and 177 score wins
with no losses against an ABC-AIG baseline on the same $n\leq 6$ export.  It
also has 177 score wins with no losses against ABC-XAG/GIA, ABC-LUT, and
BDD/Shannon baselines, and 147 score wins, 24 losses, and 6 ties against ABC's
quantum-cost ESOP minimization path.  A
resource-profile stress test shows that \paretomethod{} is best or tied on
44/47, 44/47, 42/47, and 43/47 functions under T-heavy, balanced,
CNOT-depth-heavy, and ancilla-tight objectives, improving on
\profilemethod{} with no score losses in any profile.  A larger core benchmark
through $n=12$ contains 330 functions and 1980 method/function rows; \method{}
and \profilemethod{} complete all functions, and \method{} reduces mean
T-count by 60.37\% relative to direct ANF and by 37.25\% relative to
logical-AND direct ANF, while fixed-coordinate MCTS times out on five $n=12$
rows.  An isolated
$n=14$ stress benchmark adds 64 random ANF functions and 576 rows with no
errors or skips; the Pareto high-dimensional variant reduces mean T-count by
57.94\% relative to direct ANF and by 33.30\% relative to logical-AND direct
ANF, with 60 score wins, no losses, and 4 ties against FPRM-greedy.  A
follow-up $n=15$ scale check preserves this pattern with 30 score wins, no
losses, and 2 ties against FPRM-greedy, reducing mean weighted score by
5.73--5.75\%.  A further $n=16$ scale check contains 24 random ANF functions
and 168 rows with no errors or skips; the Pareto archive reduces mean T-count
by 62.12\% relative to direct ANF and has 22 score wins, no losses, and 2 ties
against bounded FPRM root-beam.  On
a final $n=18$ stress check, 12 random ANF functions produce 84 verified rows
with no errors or skips; a fast linear-pair guard improves bounded FPRM
root-beam by 1.91\% in mean weighted score, and the guarded
Resource/Profile/Pareto variants reduce mean T-count by 60.05\% and mean
weighted score by 56.99\% relative to direct ANF, with 12 score wins and no
losses against root-beam.  On
exported high-dimensional ABC AIG/XAG/LUT and BDD checks for the same $n=14$,
$n=15$, $n=16$, and $n=18$ sets, the guarded variants win all 528
weighted-score comparisons with 93.24\%--99.69\% mean score reductions.  At
$n=18$ the mean score reductions are 98.85\% against ABC-AIG, 99.05\% against
ABC-XAG, 99.69\% against ABC-LUT, and 98.30\% against BDD.  ABC-AIG and ABC-XAG
keep lower estimated depth on most functions, while ABC-LUT and BDD are deeper
under our sequential network estimates.  The method is
evaluated only at the logical circuit layer;
hardware mapping and connectivity constraints are outside the present scope.
\end{abstract}

\section{Introduction}

Boolean oracles translate classical predicates into reversible quantum
subroutines.  In fault-tolerant settings, the cost of such oracles is often
dominated by non-Clifford resources, so synthesis methods must account for
T-count, depth, and ancillary workspace rather than only the number of reversible
gates.  Existing Boolean-oriented approaches provide strong representations and
baseline synthesis methods, while recent learning-guided circuit work shows
that neural policies and tree search can be useful in large synthesis spaces.
The gap addressed here is the combination of these two lines: a neural search
method whose state and actions remain symbolic Boolean oracle constructions and
whose objective directly scores T-count, CNOT count, depth, gates, and ancilla.

This paper frames quantum Boolean oracle synthesis as a resource-constrained
search over algebraic-normal-form (ANF) and fixed-polarity Reed--Muller (FPRM)
factorizations.  The central claim is that affine changes of Boolean coordinates
can expose low-T decompositions that fixed-coordinate ANF factoring misses, and
that a resource-adaptive neural MCTS portfolio can retain these wins while
guarding against degradation under different weighted objectives.

\section{Related Work and Gap}

Boolean-structure methods are the closest technical baselines.  XAG-based
quantum compilation uses XOR-and-AND logic networks to reduce fault-tolerant
resources; ROS combines LUT mapping with resource-aware oracle synthesis and
SAT-based garbage management; multiplicative-complexity methods relate the
number of AND nodes in a Boolean network to T-count and ancilla upper bounds;
ABC provides a mature AIG rewriting and verification baseline for Boolean logic;
and BDD-based reversible synthesis scales to large Boolean functions by
compiling decision-diagram
structure~\cite{meuli2022xag,meuli2020ros,meuli2019multiplicative,brayton2010abc,wille2009bdd}.
SSHR is also closely related because it exploits parallelotope structure in the
Boolean hypercube and provides CNOT-oriented small-function baselines,
including heuristic and ILP variants~\cite{zheng2025sshr}.  These methods
motivate the resource metrics and symbolic action space used here, but they do
not use a learned policy/value search over ANF/FPRM factorization plans.

Learning-guided synthesis has developed along adjacent axes.  ShortCircuit uses
an AlphaZero-style process for classical AIG generation from truth tables,
showing that policy/value search can help Boolean circuit construction at the
logic level~\cite{tsaras2024shortcircuit}.  Quantum learning-guided work has
used Gumbel AlphaZero for Clifford+T unitary synthesis, reinforcement learning
for non-Clifford-count optimization, MCTS for Hamiltonian-simulation Pauli-term
ordering, and PPO/GNN policies for ZX-calculus rewriting~\cite{rietsch2024unitary,kremer2025nonclifford,machiya2026monteq,riu2025rlzx}.
These systems validate the use of neural search in synthesis, but they do not
directly target Boolean oracle factorization with explicit T/CNOT/depth/ancilla
tradeoffs.

The present method therefore avoids two weak directions for this problem: it is
not a gate-by-gate unitary generator, and it is not an SSHR parallelotope
selector.  It searches over reusable Boolean intermediates in ANF/FPRM form,
uses affine coordinate changes as a cheap way to alter the factorization basis,
and treats external XAG, ROS, BDD, ESOP, and SSHR-style flows as baselines or
export targets rather than as components of the method.

\section{Problem Formulation}

Let $f:\{0,1\}^n\rightarrow\{0,1\}$ be a Boolean function.  The target oracle
maps
\[
  |x\rangle |y\rangle \mapsto |x\rangle |y \oplus f(x)\rangle .
\]
We represent $f$ by its ANF,
\[
  f(x) = \bigoplus_{m\in M}\prod_{i\in m} x_i,
\]
where each monomial is encoded as a bit mask.  Direct ANF synthesis applies one
controlled operation per monomial.  The search problem is to replace this direct
construction by reusable compute/uncompute subplans that lower the weighted
resource score
\[
  S = w_T T + w_C CNOT + w_D D + w_G G + w_A A,
\]
where $T$ is T-count, $D$ is logical depth, $G$ is gate count, and $A$ is peak
ancilla.

\section{Method}

\subsection{Resource-aware ANF factorization}

At each search state, the remaining ANF terms are a set of monomial masks.  An
action chooses a common factor $S$ appearing in at least two terms, computes
$S$ into a clean temporary ancilla, synthesizes the residual terms using that
ancilla as an additional control, uncomputes $S$, and then synthesizes the
remaining terms.  The implementation restricts the number of live factor
ancillae and ranks candidate factors by immediate weighted resource gain.

\subsection{Logical-AND cost model}

The reported resource objective uses a logical-AND accounting mode: temporary
ANDs are charged four T gates for compute and T-free Clifford/measurement-based
cleanup for uncompute.  The verifier circuit remains deterministic and is
checked by exhaustive classical simulation over the truth table.  Thus the
paper reports logic-level resource estimates rather than mapped hardware
circuits.

\subsection{Neural Monte Carlo tree search}

The MCTS solver recursively applies PUCT-style selection to factorization
actions.  Unvisited subproblems use a greedy rollout value.  A small neural
action scorer is trained from synthetic ANF states with rollout-improvement
labels, then used as an additive prior during action ranking.

\subsection{Affine Boolean preconditioning}

\affinemethod{} searches invertible linear transforms $y=Bx$ before ANF/FPRM
factorization.  For each candidate transform, it synthesizes
$h(y)=f(B^{-1}y)$ and wraps the body circuit by CNOT networks implementing and
undoing $B$.  Candidate transforms include the identity, star-like XOR
transforms, single-CNOT transforms, and random short CNOT sequences.  The
candidate list is first ranked by fast FPRM/greedy factoring; low-dimensional
instances are then refined by neural MCTS, while large instances use term-count
guards to avoid affine densification.

\subsection{Guard against fixed-coordinate degradation}

The affine plan is compared against a fixed-coordinate MCTS plan under the same
weighted score.  The lower-score plan is returned.  This guard makes the method
nondegrading in score on completed fixed-coordinate MCTS pairs, while preserving
affine improvements when coordinate changes reveal better factorizations.

\subsection{Resource-adaptive portfolio guard}

The full \method{} solver treats the weighted resource objective as a selection
criterion over internally generated candidates.  For each function it evaluates
direct ANF, FPRM/greedy factoring, and a budgeted \affinemethod{} candidate.
When the configured dimension guard permits it, the portfolio also evaluates
fixed-coordinate logical-AND MCTS; for $n\leq 6$, it additionally evaluates
ESOP cube-beam search.  For $n>12$, where full fixed-coordinate MCTS and broad
affine search create long tails, it replaces the expensive branches by a
bounded recursive FPRM linear-pair candidate: many polarities are screened by
direct cost, a root-child beam baseline is retained, and repeated term pairs
$x_i m \oplus x_j m$ can be factored as $(x_i \oplus x_j)m$ using a temporary
CNOT-computed linear control.  One extra recursive layer applies the same pair
search to both the quotient and the remaining terms when the subproblem has at
most 900 terms.
It returns the correct candidate with the smallest
weighted score, breaking ties by T-count, CNOT count, depth, and peak ancilla.
SSHR is used only as an external baseline in the experiments and is not part of
this portfolio.  This final guard converts the affine neural search into a
resource-constrained synthesis method: when affine coordinates are best, they
are retained; when a simpler internal construction is better under the active
weights, the method can select it.  The guard is budgeted rather than an
all-scale dominance certificate: high-dimensional runs deliberately avoid
internal candidates that create long runtime tails.

\subsection{Profile-aware candidate generation}

\profilemethod{} adds a second portfolio layer for explicit resource profiles.
For $n\leq 6$, it evaluates additional T-aggressive, CNOT/depth-oriented, and
ancilla-tight FPRM, affine-greedy, and ESOP cube-beam candidates before
selecting by the active weighted score.  For larger random-ANF instances, the
same method delegates to the high-dimensional Resource-NMCTS guard: it keeps
direct ANF and the bounded recursive FPRM linear-pair candidate, but avoids
expensive fixed-coordinate MCTS guards.  A width-three linear-parity factor is
reported as a standalone ablation in the $n=15$ scaling check, but the
portfolio uses the recursive pair candidate because it dominates the parity
ablation under the weighted objective.
This design separates two roles.  On small functions it tests whether the
resource profile can change the selected circuit; on large functions it acts as
a runtime-tail guard rather than a score-dominance guarantee.

\subsection{Pareto resource archive}

\paretomethod{} strengthens the small-function resource-profile search by
changing the internal objective used to generate candidates, not only the
search budget.  For each function it evaluates child searches under five
candidate-generation objectives: the active score, a T-sparse score, a
CNOT/depth-heavy score, an ancilla-tight score, and a gate-count-sensitive
score.  The resulting candidates include FPRM greedy, bounded root-child beam,
CNOT-only linear-pair factoring, affine-greedy, selected affine-neural, and
ESOP cube-beam plans when the dimension guard permits them.  The method then
removes candidates dominated simultaneously in T-count, CNOT count, depth,
gate count, and peak ancilla, and finally selects from this non-dominated
archive using the active resource profile.  Thus the method keeps the same
logical verifier and cost model as \method{}, but explicitly approximates a
local Pareto frontier before profile-specific selection.
On $n\leq 6$ functions, the archive also includes a ranked polarity candidate:
all $2^n$ FPRM polarities are screened under greedy, root-child-beam, and
CNOT-only linear-pair factorizations, and the best scored plan is added to the
non-dominated pool.

\section{Experiments}

\subsection{Benchmark and baselines}

The current \dataset{} run contains 322 Boolean functions: structured oracles
such as parity, majority, threshold, mux, adders, and multipliers; random truth
tables for $n=4,5,6$; and random ANF functions for $n=8,10,12$.  We compare:
direct ANF, logical-AND direct ANF, fixed-coordinate logical-AND MCTS,
\affinemethod{}, and SSHR-H for functions with $n\leq 6$.
A separate \traditionaldataset{} slice restricts the benchmark to $n\leq 6$
and adds \method{}, ESOP cube beam search, and a time-limited weighted ESOP
MILP over candidate cubes.  The \largedataset{} benchmark extends the same
resource objective to a larger random-ANF core through $n=12$.  To support
external reproduction, the benchmark generator can export every preset to PLA,
BLIF \texttt{.names}, and truth-table JSON manifests.  The current draft adds
an exported exact-SSHR-I pilot on the $n\leq 4$ subset, a time-limited
$n\leq 6$ SSHR-I extension, Berkeley ABC AIG, XAG/GIA, LUT, and ESOP
baselines, and a reduced ordered BDD baseline covering the full
\traditionaldataset{} slice.  The ABC-AIG, ABC-XAG, ABC-LUT, and BDD export
paths are also run on the isolated $n=14$, $n=15$, and $n=16$
high-dimensional random-ANF suites; reproduced ROS/mockturtle
reversible-toolchain results are still future work.

\subsection{Main results}

\begin{table}[t]
\centering
\caption{Current \dataset{} results.  Improvements are relative T-count means
over functions where both methods completed.}
\label{tab:main-results}
\begin{tabular}{lrrrr}
\toprule
Comparison & Functions & Wins & Ties & Mean $\Delta T$ \\
\midrule
\affinemethod{} vs direct ANF & 322 & 286 & 36 & $-61.83\%$ \\
\affinemethod{} vs logical-AND direct ANF & 322 & 284 & 38 & $-40.12\%$ \\
\affinemethod{} vs fixed-coordinate MCTS & 321 & 161 & 160 & $-16.18\%$ \\
\affinemethod{} vs SSHR-H & 177 & 171 & 5 & $-43.89\%$ \\
\bottomrule
\end{tabular}
\end{table}

\affinemethod{} was correct on all 322 functions.  Fixed-coordinate MCTS timed
out on one $n=12$ random ANF function after a 600 s repair attempt;
\affinemethod{} completed the same function within the experiment budget and
produced a valid circuit.
The largest direct-ANF reductions exceeded 80\% T-count on several structured
and random small functions.

\subsection{Traditional ESOP baselines}

The \traditionaldataset{} slice tests whether the gain persists against
traditional Boolean/ESOP-style synthesis rather than only direct ANF and MCTS
variants.  It contains 177 functions with $n\leq 6$ and ten methods,
producing 1770 method/function rows with no errors or skips.  On this slice,
\paretomethod{} had the lowest mean T-count and the lowest mean composite
score among all tested methods.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on the \traditionaldataset{} slice.  ESOP MILP
is a time-limited weighted ESOP optimization over candidate cubes.}
\label{tab:traditional-resources}
\input{tables/resource_traditional_resource}
\end{table}

The ESOP-focused aggregate in Table~\ref{tab:esop-by-n} is the same-benchmark
comparison corresponding most closely to the ESOP column used in prior
small-function studies.  It should not be read as a direct numerical
comparison to published ESOP totals from a different function set or cost
model.

\begin{table}[t]
\centering
\scriptsize
\caption{ESOP-centered aggregate comparison by variable count on the matched
$n\leq 6$ benchmark.  T/C/A denotes total T-count, total CNOT count, and summed
peak-ancilla count across functions in the group.  Negative changes favor
\paretomethod{}.}
\label{tab:esop-by-n}
\input{tables/esop_baseline_by_n}
\end{table}

Against \method{}, \paretomethod{} had 74 score wins, no score losses, and 103
ties, with a 4.59\% mean composite-score reduction.  Against ESOP cube beam
search, \paretomethod{} had 174 score wins, no losses, and 3 ties, with a
35.86\% mean composite-score reduction.  Against weighted ESOP MILP,
\paretomethod{} had 167 score wins, 3 losses, and 7 ties, with a 29.61\% mean
composite-score reduction.  Against SSHR-H, \paretomethod{} had 173 T-count
wins, no T-count losses, 4 ties, and 173 score wins with 4 score losses.
SSHR-H retained the lowest mean CNOT count on this small-function slice, so
this result supports low-T and weighted-resource synthesis rather than
CNOT-only optimality.
The aggregate ESOP comparison is stronger than the per-function win/loss
counts alone: against internal ESOP-MILP, \paretomethod{} lowers total T-count
by 51.23\%, CNOT count by 37.13\%, and summed peak ancilla by 15.09\%.  Against
external ABC-ESOP, it lowers total T-count by 25.18\%, CNOT count by 4.38\%,
and summed peak ancilla by 14.04\%.  The only aggregate CNOT counterexample is
the $n=6$ ABC-ESOP group, where \paretomethod{} uses 7097 CNOTs versus 7068 for
ABC-ESOP, a 0.41\% increase, while still reducing T-count, peak ancilla, and
weighted score.

\subsection{Exported external baselines}

To check the external-tool exchange path, we exported the
\traditionaldataset{} benchmark to PLA, BLIF, and truth-table JSON, then ran
separate external backends over the exported manifest.  The SSHR backend gives
CNOT-oriented heuristic and ILP baselines.  The ABC-AIG backend optimizes the
exported BLIF with ABC rewriting, verifies the optimized BLIF truth table, and
maps AIG AND count and level to a logic-level Bennett compute/uncompute
resource estimate.  The ABC-XAG backend uses ABC's GIA \texttt{\&st -m -L 1}
path, records XOR/MUX/AND statistics with \texttt{\&ps -m -x}, verifies the
emitted BLIF truth table, and scores the network with a Bennett-style logical
XAG estimate.  The ABC-ESOP backend runs ABC's quantum-cost
\texttt{\&exorcism -q} flow, verifies the emitted ESOP-PLA against the exported
truth table, and scores the resulting XOR-of-cubes oracle using the same
logical-AND cube model as the internal ESOP baselines.  The ABC-LUT backend maps
the same BLIF through \texttt{if -K 4}, verifies the mapped BLIF, and scores a
compute/output/uncompute network whose local LUT functions are converted to
ANF terms.  The BDD backend builds reduced ordered BDDs under several
deterministic variable orders, verifies the decision diagram against the
exported truth table, and scores a
compute/uncompute Shannon network.  For the 72 functions
with $n\leq 4$, the SSHR-I runs are
exact within the configured Gurobi solve.  This exact pilot produced 216
external rows with no errors or skips and confirmed that \method{} retains a
weighted-score advantage against both CNOT-optimized and T-optimized SSHR-I,
while spending more CNOTs.

\begin{table}[t]
\centering
\small
\caption{\method{} compared with exported external baselines on the
177-function $n\leq 6$ extension.  SSHR-I rows use an 8 s per-call Gurobi
budget.  ABC-AIG rows use verified ABC-optimized BLIF and Bennett-style
resource estimates; ABC-XAG rows use verified ABC GIA/XOR-aware BLIF and
logical XAG estimates; ABC-LUT rows use verified LUT-mapped BLIF and local-ANF
node estimates; BDD rows use verified reduced ordered BDDs and Shannon-network
estimates; ABC-ESOP rows use verified \texttt{\&exorcism -q} ESOP-PLA and
logical-AND cube estimates.  Wins/losses/ties count common
functions; negative mean relative values favor \method{}.}
\label{tab:external-baselines}
\input{tables/external_traditional_resource_n6}
\end{table}

The exact $n\leq 4$ pilot strengthens but also sharpens the claim.  Against
CNOT-optimized SSHR-I, \method{} has 65 T-count wins, no T-count losses, and 7
ties; by weighted score it has 69 wins, 3 losses, and no ties, with a 26.45\%
mean score reduction.  Against T-optimized SSHR-I it shows the same T-count
win/tie pattern and a 26.21\% mean score reduction.  In both exact comparisons,
however, \method{} loses CNOT count on most functions.  This supports the
resource-constrained low-T oracle-synthesis claim, while ruling out any
CNOT-only optimality claim.

We then ran the external extension over all 177 exported functions with
$n\leq 6$.  This produced 1416 external rows with no errors or skips: 531 SSHR
rows, 177 ABC-AIG rows, 177 ABC-XAG rows, 177 ABC-LUT rows, 177 BDD rows, and
177 ABC-ESOP rows.
Against the CNOT-optimized SSHR-I extension, \method{} had 164 T-count wins, 3
losses, and 10 ties, and 168 score wins with
9 score losses; the mean score reduction was 27.92\%.  Against the T-optimized
extension, \method{} had 166 T-count wins, 1 loss, and 10 ties, with a 26.25\%
mean score reduction.  The CNOT disadvantage persisted, with \method{} worse on
168/177 CNOT comparisons against the CNOT-optimized run.

The ABC-AIG comparison strengthens the resource-constrained claim from a
different direction.  \method{} had 170 T-count wins, 2 losses, and 5 ties
against ABC-AIG; it won all 177 CNOT, peak-ancilla, and weighted-score
comparisons, reducing mean weighted score by 54.52\% and mean peak ancilla by
86.29\%.  ABC-AIG had a lower depth estimate on 126/177 functions, which is
consistent with a shallow optimized AIG followed by a wide Bennett embedding.
This makes ABC-AIG a useful foil for the ancilla and weighted-resource
objective, not a claim that \method{} dominates every metric.

The ABC-XAG/GIA comparison adds an XOR-aware network baseline without using an
external mapper inside the method.  \method{} had 176 T-count wins, no losses,
and 1 tie against ABC-XAG; it won all 177 peak-ancilla and weighted-score
comparisons, reducing mean weighted score by 63.23\% and mean peak ancilla by
89.85\%.  It also reduced mean CNOT by 35.53\%, although ABC-XAG retained a
lower depth estimate on 144/177 functions.  This closes part of the earlier
XAG comparison gap while still falling short of a full ROS or mockturtle
reversible-toolchain reproduction.

The ABC-LUT comparison adds a mapped-LUT network baseline closer to ROS/LUT
families, though still without a full reversible LUT mapper.  \method{} won all
177 CNOT, depth, peak-ancilla, and weighted-score comparisons against ABC-LUT,
with 175 T-count wins and 2 ties.  The mean weighted-score reduction was
76.41\%.  This result shows that a naive compute/uncompute embedding of
LUT-mapped BLIF is not competitive under the current logical-resource model,
but it narrows the external LUT comparison gap.

The BDD comparison adds a scalable decision-diagram baseline.  \method{} won
all 177 T-count, CNOT, depth, peak-ancilla, and weighted-score comparisons
against BDD, reducing mean weighted score by 67.15\%.  This result should be
read as a comparison to a verified logic-level Shannon-network embedding of
ROBDDs rather than to every optimized BDD-based reversible synthesis variant.

The ABC-ESOP comparison is closer to the XOR-of-products synthesis family.
\method{} had 144 T-count wins, 19 losses, and 14 ties against ABC-ESOP, and
147 score wins, 24 losses, and 6 ties.  The mean weighted-score reduction was
19.88\%; unlike the SSHR-I CNOT-oriented comparison, \method{} also had a small
mean CNOT reduction of 1.19\%.  This result is not a substitute for a reproduced
ROS mapper, but it adds a standard external XOR/ESOP minimizer to the
comparison boundary.
The stronger small-function \paretomethod{} setting improves this ESOP boundary:
on the same ABC-ESOP rows it has 170 score wins, 1 score loss, and 6 ties, with
a 23.00\% aggregate score reduction.  Its aggregate T-count and peak-ancilla
sums are lower in every $n=3,\ldots,6$ group; aggregate CNOT is lower through
$n=5$ and nearly tied at $n=6$.

Finally, we pushed the ABC AIG/XAG/LUT and BDD exchange beyond the small-function
slice.  The \highdimdataset{}, \scaledataset{}, \ultradataset{}, and
\megadataset{} suites were
exported to BLIF/truth JSON, optimized or represented by the external-style
baselines, and verified by a bit-parallel full truth-table checker before
scoring.  The high-dimensional rows contain 64 $n=14$, 32 $n=15$, 24 $n=16$,
and 12 $n=18$ functions for each of ABC-AIG, ABC-XAG, ABC-LUT, and BDD, all
correct and with no errors or skips.  Against all four baselines, \method{},
\profilemethod{}, and \paretomethod{} win every T-count, CNOT, peak-ancilla,
and weighted-score comparison across these 528 external rows; the mean
score reductions range from 93.24\% to 99.69\%.  At $n=18$, the weighted-score
reductions are
98.85\% against ABC-AIG, 99.05\% against ABC-XAG, 99.69\% against ABC-LUT, and
98.30\% against BDD.  The depth column remains an important counterweight for
ABC: ABC-AIG has a lower estimated depth on 50/64, 25/32, 22/24, and 10/12
functions across the four high-dimensional suites, and ABC-XAG has a lower
estimated depth on 50/64, 26/32, 22/24, and 11/12 functions, respectively.
ABC-LUT and BDD
depths are much higher under the sequential network estimates.  Thus the
high-dimensional external result supports the low-ancilla and weighted-resource
claim, but not depth-only dominance against optimized ABC networks.

\begin{table}[t]
\centering
\small
\caption{\method{} compared with exported ABC-AIG, ABC-XAG, ABC-LUT, and BDD baselines
on the high-dimensional $n=14$ and $n=15$ random-ANF suites.  Rows use verified
ABC-optimized or LUT-mapped BLIF, or verified reduced ordered BDDs, with
logic-level resource estimates.  Negative mean relative values favor \method{}.}
\label{tab:external-highdim-aig}
\input{tables/external_highdim_abc_aig}
\end{table}

\begin{table}[t]
\centering
\small
\caption{\method{} compared with exported ABC-AIG, ABC-XAG, ABC-LUT, and BDD
baselines on the \ultradataset{} $n=16$ scale check.  Score columns report
weighted-score wins/losses/ties and mean relative score.  Depth columns expose
the ABC depth counterweight.}
\label{tab:external-ultra}
\input{tables/external_ultra_highdim_resource}
\end{table}

\begin{table}[t]
\centering
\small
\caption{\method{} compared with exported ABC-AIG, ABC-XAG, ABC-LUT, and BDD
baselines on the \megadataset{} $n=18$ stress check.  Score columns report
weighted-score wins/losses/ties and mean relative score.  Depth columns expose
the ABC depth counterweight.}
\label{tab:external-mega}
\input{tables/external_mega_highdim_resource}
\end{table}

\subsection{Ablation}

The \ablationdataset{} run used the same 322-function suite and added two
variants: affine-greedy, which performs affine transform search followed by
FPRM/greedy factoring, and affine-no-guard, which adds neural refinement but
does not compare against fixed-coordinate MCTS.  This ablation separates the
effect of coordinate search, neural refinement, and the final guard.

\begin{table}[t]
\centering
\caption{Ablation results on the same 322-function suite.  Wins, ties, and
losses use the composite resource score unless otherwise stated.}
\label{tab:ablation}
\begin{tabular}{lrrrr}
\toprule
Comparison & Wins & Ties & Losses & Mean relative score \\
\midrule
\affinemethod{} vs affine-greedy & 153 & 169 & 0 & $-2.82\%$ \\
affine-no-guard vs affine-greedy & 65 & 257 & 0 & $-1.08\%$ \\
\affinemethod{} vs affine-no-guard & 88 & 234 & 0 & $-1.74\%$ \\
\affinemethod{} vs fixed-coordinate MCTS & 165 & 156 & 0 & $-14.82\%$ \\
\bottomrule
\end{tabular}
\end{table}

Affine-greedy alone reduced mean T-count by 60.92\% relative to direct ANF,
showing that the affine coordinate search is the dominant contributor.  Neural
refinement and the guard were smaller but monotone under the composite score:
neither introduced score losses on the benchmark.

We also reran the $n\leq 6$ \traditionaldataset{} slice with the learned action
scorer removed while keeping the same heuristic PUCT/action prior.  The paired
comparison contains 1062 rows over \affinemethod{}, \method{}, and
\paretomethod{}, with no errors or skips.  The learned prior gives modest but
monotone score improvements: 42/0/135 score wins/losses/ties for
\affinemethod{}, 41/0/136 for \method{}, and 29/0/148 for \paretomethod{}.
Mean score reductions are 1.47\%, 1.34\%, and 0.78\%, respectively.  The cost
is runtime: the paired mean relative runtime increases are 91.22\%, 87.31\%,
and 67.44\%, because many small neural action batches are evaluated on CPU.
We therefore treat the learned prior as a quality-improving search signal, not
as the current fastest mode.

\begin{table}[t]
\centering
\small
\caption{Learned-prior ablation on the $n\leq 6$ \traditionaldataset{} slice.
Rows compare the learned action scorer against the same search with only the
heuristic action prior.  Negative mean score change favors the learned prior.}
\label{tab:neural-prior-ablation}
\input{tables/neural_prior_ablation}
\end{table}

Table~\ref{tab:contribution-decomposition} consolidates the scattered
ablation evidence into one matched-pair contribution account.  The strongest
pre-portfolio algorithmic step is affine coordinate search: affine-greedy
already reduces the composite score by 12.12\% relative to completed
fixed-coordinate MCTS pairs, albeit with score losses on some functions.  The
neural refinement and final guard are smaller but monotone in score on this
suite, and the learned prior gives a positive no-loss quality signal on the
$n\leq 6$ rerun.  The table also clarifies the high-dimensional claim.  At
$n=14$--$n=18$, most of the measurable scale gain comes from bounded
linear-pair guards and their recursive/fast variants; Pareto or Resource
selection provides additional separation in some suites, but should not be
described as a large independent archive effect when it ties the guarded child.

\begin{table}[t]
\centering
\scriptsize
\caption{Contribution decomposition from matched function-level comparisons.
Wins/losses/ties use the composite resource score.  Negative mean score change
favors the component in the first column.}
\label{tab:contribution-decomposition}
\input{tables/search_contribution_decomposition}
\end{table}

\subsection{Runtime and resource tradeoff}

The ablation also exposes the computational cost of the search components.
Affine-greedy completed all 322 functions with a 0.03 s median runtime and a
1.82 s maximum runtime, while the full \affinemethod{} method had a 0.61 s median
runtime and a 300.02 s maximum runtime because it invokes the fixed-coordinate
MCTS guard.  Fixed-coordinate MCTS timed out on one $n=12$ function, whereas all
affine variants completed every function.

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \ablationdataset{} suite.  SSHR-H is
skipped for $n>6$ by the harness.}
\label{tab:runtime}
\input{tables/runtime_ablation_affine}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on completed rows in the \ablationdataset{}
suite.  SSHR-H means are over its supported $n\leq 6$ subset and therefore are
not directly comparable to all-suite means.}
\label{tab:resources}
\input{tables/resource_ablation_affine}
\end{table}

\subsection{Resource-profile stress test}

To test whether the method remains competitive under different resource
objectives, we ran a 47-function $n\leq 6$ sweep under four profiles: T-heavy,
balanced, CNOT-depth-heavy, and ancilla-tight.  The sweep produced 1692
method/profile/function rows with no errors or skips.  Scores are comparable
within a profile but not across profiles because each profile uses a different
weighted objective.

\begin{table}[t]
\centering
\small
\caption{Objective-score best-or-tied counts in the resource-profile sweep.
Rows may sum to more than 47 because several methods can achieve the same
minimum score on a function.}
\label{tab:resource-sweep-winners}
\input{tables/resource_sweep_winners}
\end{table}

\paretomethod{} was best or tied on 44/47 functions under T-heavy weights,
44/47 under balanced weights, 42/47 under CNOT-depth-heavy weights, and 43/47
under ancilla-tight weights.  Relative to \profilemethod{}, it had score
wins/losses/ties of 19/0/28, 19/0/28, 21/0/26, and 15/0/32 across the four
profiles, with mean score reductions of 5.56\%, 4.93\%, 4.85\%, and 2.51\%.
Relative to \method{}, it also had no score losses in any profile.  The mean
\paretomethod{} resource vector changed with the active objective: mean
T-count stayed at 35.91 for T-heavy, balanced, and CNOT-depth profiles and rose
to 39.74 under ancilla-tight weights, while mean peak ancilla fell from
1.87--1.94 to 1.62 in the ancilla-tight profile.  This result shows that
objective-specific candidate generation and non-dominated archive selection
produce a stronger profile-sensitive Pareto search than the earlier bounded
profile portfolio.

\subsection{Large-scale core benchmark}

The \largedataset{} run contains 330 functions, including structured oracles,
random truth-table functions up to $n=6$, and random ANF functions up to
$n=12$.  It produces 1980 method/function rows under process-isolated hard
timeouts on an Apple M4 Pro workstation with 14 logical CPU cores and 24 GB
memory.  Direct ANF, logical-AND direct ANF, \affinemethod{}, \method{}, and
\profilemethod{} complete all 330 functions; fixed-coordinate MCTS completes
325 functions and times out on five $n=12$ random ANF rows.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on completed rows in the \largedataset{}
benchmark.  The fixed-MCTS mean excludes five timeout rows, so its completed-row
average is censored toward easier instances.}
\label{tab:large-resources}
\input{tables/resource_large_resource_core}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \largedataset{} benchmark.}
\label{tab:large-runtime}
\input{tables/runtime_large_resource_core}
\end{table}

On this larger suite, \method{} reduces mean T-count by 60.37\% versus direct
ANF and by 37.25\% versus logical-AND direct ANF.  The corresponding
composite-score reductions are 56.84\% and 35.21\%.  Against completed
fixed-coordinate MCTS pairs, \method{} has 139 T-count wins, 15 losses, and 171
ties, with an 11.41\% mean composite-score reduction.  This comparison should
be interpreted with the five fixed-MCTS timeouts in mind: the completed-row
mean for fixed MCTS excludes its hardest rows, whereas \method{} completed all
functions.  Relative to standalone \affinemethod{}, the budgeted portfolio has
29 score wins, 16 score losses, and 285 ties, with a 0.20\% mean score
reduction.  Thus the portfolio is useful as a scalable resource-aware guard,
but it is not a dominance guarantee over the full affine search when
high-dimensional instances force tighter candidate budgets.  \profilemethod{}
has a lower runtime tail than \method{} on this suite, with p95 runtime 25.68 s
versus 58.86 s, but its cheap high-dimensional guard increases mean score from
273.72 to 286.54.  We therefore treat it as a profile-sensitive and
tail-reducing extension, not as the large-scale score winner.

\subsection{High-dimensional n=14 stress test}

The \highdimdataset{} run isolates high-dimensional random ANF instances rather
than mixing them with small structured functions.  It contains 64 $n=14$
functions and nine methods, for 576 method/function rows with no errors or
skips.  This experiment uses the high-dimensional guard described above:
fixed-coordinate MCTS and broad affine search are avoided inside the guarded
methods, while direct ANF, bounded FPRM root-child beam, linear-pair candidates,
and bounded Pareto archive variants remain available.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on the \highdimdataset{} $n=14$ stress
benchmark.}
\label{tab:highdim-resources}
\input{tables/resource_highdim_resource}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \highdimdataset{} $n=14$ stress
benchmark.}
\label{tab:highdim-runtime}
\input{tables/runtime_highdim_resource}
\end{table}

The Resource/Profile/Pareto guarded methods complete all 64 functions.
Relative to direct ANF, \paretomethod{} has 61 T-count wins, no losses, and 3
ties, with a 57.94\% mean T-count reduction and a 54.55\% mean composite-score
reduction; \method{} and \profilemethod{} have the same win/tie pattern with
57.43\% and 54.01\% reductions.  Relative to logical-AND direct ANF,
\paretomethod{} again has 61 score wins, no losses, and 3 ties, with a 31.40\%
mean score reduction.  Against FPRM-greedy, the guarded methods have 60
weighted-score wins, no losses, and 4 ties, with 6.29--6.83\% mean score
reductions.  Against the standalone FPRM root-beam candidate, \paretomethod{}
has 60 score wins, no losses, and 4 ties, with a 6.31\% mean score reduction.
Against the active Resource/Profile candidates, \paretomethod{} gives 16 score
wins, no losses, and 48 ties, reducing mean score by 0.59\%.  The mean T-count
falls from 2263.69 for FPRM-greedy, 2248.81 for root beam, and 2193.50 for
one-layer linear pair to 2149.50 for \method{} and 2148.81 for
\paretomethod{}.  The improvement is mechanistically different from simply
widening the root beam: the recursive linear-pair candidate computes
$x_i \oplus x_j$ into a temporary ancilla with CNOTs, factors the paired
residual subplan under that control, and then recursively searches the quotient
and bounded rest subproblems before uncomputing the linear control.  Runtime
tails remain bounded but increase: \method{} has median runtime 8.57 s and
p95 runtime 80.43 s, \profilemethod{} has median runtime 9.29 s and p95
runtime 84.23 s, while \paretomethod{} has median
runtime 67.79 s and p95 runtime 300.02 s.  The resource tradeoff is workspace:
mean peak ancilla increases from 2.03 for FPRM-greedy and root beam to about
3.05--3.06 for the guarded variants.

As a scale check, we also run the same high-dimensional guard on 32 random
$n=15$ ANF functions, producing 320 method/function rows with no errors or
skips after adding the bounded recursive linear-pair candidate, a standalone
width-three linear-parity ablation, and a bounded Pareto archive.  Relative to
FPRM-greedy, the Resource/Profile/Pareto guarded variants have 30 T-count
wins, no losses, and 2 ties, with 6.89--6.93\% mean T-count reductions and
5.73--5.75\% mean score reductions.  Relative to the standalone FPRM
root-beam candidate, they have 30 score wins, no losses, and 2 ties, with
5.28--5.31\% mean score reductions.  The recursive pair candidate is a
material refinement of the one-layer linear-pair search: it improves weighted
score in 29 cases, ties in 3, and has no score losses, while increasing mean
peak ancilla from 2.84 to 3.06.  The Pareto archive extracts a smaller
residual gain over the active Resource/Profile candidates, with 5 score wins,
no losses, 27 ties, and a 0.03\% mean score reduction.  Runtime remains finite
under the 900-term recursion guard: \method{} has median runtime 9.70 s and
p95 runtime 90.02 s, \profilemethod{} has median runtime 11.33 s and p95
runtime 93.68 s, and \paretomethod{} has median runtime 117.52 s and p95
runtime 300.30 s.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on the \scaledataset{} $n=15$ scaling check.}
\label{tab:scale-resources}
\input{tables/resource_highdim_scale_resource}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \scaledataset{} $n=15$ scaling check.}
\label{tab:scale-runtime}
\input{tables/runtime_highdim_scale_resource}
\end{table}

The additional \ultradataset{} run checks whether the same guard remains usable
one dimension higher.  It contains 24 random ANF functions at $n=16$, seven
methods, and 168 method/function rows with no errors or skips.  For this
dimension the ultra-scale Resource/Profile guard deliberately disables the
recursive rest-branch linear-pair refinement used at $n=15$ and keeps the
one-layer FPRM linear-pair candidate.  Consequently \method{} and
\profilemethod{} match the standalone linear-pair candidate on all 24
functions, while \paretomethod{} adds bounded profile variants around the same
high-dimensional candidate set.  Relative to direct ANF, \paretomethod{} has
23 T-count wins, no losses, and 1 tie, reducing mean T-count by 62.12\% and
mean weighted score by 59.56\%.  Relative to logical-AND direct ANF, it has
23 score wins, no losses, and 1 tie, with a 31.75\% mean score reduction.
Relative to FPRM root-beam, it has 22 score wins, no losses, and 2 ties, with
a 1.97\% mean score reduction.  Against the active Resource/Profile candidates,
\paretomethod{} gives 9 score wins, no losses, and 15 ties, reducing mean score
by 0.09\%.  The tradeoff remains CNOT/depth against plain direct ANF, where the
lower-T factored plans use more linear Clifford work, but they reduce both CNOT
and depth relative to logical-AND direct ANF; the Pareto archive also increases
median runtime to 130.92 s.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on the \ultradataset{} $n=16$ scale check.}
\label{tab:ultra-resources}
\input{tables/resource_ultra_highdim_resource}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \ultradataset{} $n=16$ scale check.}
\label{tab:ultra-runtime}
\input{tables/runtime_ultra_highdim_resource}
\end{table}

The \megadataset{} run pushes the same harness two more variables beyond the
ultra check.  It contains 12 random $n=18$ ANF functions and seven methods,
for 84 method/function rows with no errors or skips.  This is presented as a
runtime-boundary stress test rather than a new Pareto-archive separation.  The
standalone fast FPRM linear-pair guard has 6 score wins, no losses, and 6 ties
against bounded FPRM root-beam, reducing mean weighted score by 1.91\%.  The
guarded Resource/Profile/Pareto variants then improve that fast child on all
12 functions, reducing mean weighted score by another 3.55\%.  Relative to
direct ANF, these guarded variants have 12 T-count wins, no losses, and no
ties, reducing mean T-count by 60.05\% and mean weighted score by 56.99\%.
Relative to bounded FPRM root-beam, they have 12 score wins, no losses, and no
ties, with a 5.29\% mean score reduction.  The price is runtime: median
guarded runtime is about 83.3--83.5 s and p95 runtime is about 172.9--173.8 s.

\begin{table}[t]
\centering
\small
\caption{Mean logical resources on the \megadataset{} $n=18$ stress check.}
\label{tab:mega-resources}
\input{tables/resource_mega_highdim_resource}
\end{table}

\begin{table}[t]
\centering
\small
\caption{Runtime distribution on the \megadataset{} $n=18$ stress check.}
\label{tab:mega-runtime}
\input{tables/runtime_mega_highdim_resource}
\end{table}

\section{Discussion}

The results support the central hypothesis that affine Boolean coordinates are
a useful search dimension for quantum oracle synthesis and that a
resource-adaptive internal portfolio can reduce avoidable score regressions
under explicit budget guards.
The wins are strongest in T-count and composite resource score.  Against
SSHR-H, the method often uses more CNOTs and depth, which is expected because
SSHR-H is a CNOT-oriented small-function baseline and is not included in the
\method{} portfolio.  The present contribution should therefore be framed as
low-T, resource-constrained logical synthesis, not as a CNOT-only optimizer.

The runtime results show a practical tradeoff.  Affine-greedy captures most of
the T-count gain at very low runtime, making it the best fast setting in the
current implementation.  \method{} is slower than \affinemethod{} on the
$n\leq 6$ slice because it evaluates additional internal candidates, but its
median runtime remains below 1 s in the current small-function experiment.  On
the \largedataset{} benchmark, \method{} completes every function with median
runtime 1.31 s and p95 runtime 58.86 s; the fixed-coordinate MCTS baseline has
five timeouts.  The guarded \profilemethod{} variant reduces the p95 runtime to
25.68 s on the same large benchmark, at the cost of a higher mean score.  On
the isolated $n=14$ stress test, the Resource/Profile/Pareto guarded variants
complete all 64 functions and improve over FPRM-greedy with no score losses;
the $n=16$ scale check also completes without errors after switching to the
ultra-scale one-layer linear-pair guard and adding a bounded Pareto archive.
The $n=18$ stress check completes all 84 rows after switching to a fast
linear-pair high-dimensional guard, and the guarded Resource/Profile/Pareto
variants improve bounded root-beam on all 12 functions while keeping
minute-scale runtime tails.  This shows that
the current high-dimensional guard is no longer only a scalability fallback:
pairwise XOR factoring can correct a measurable part of the greedy
Reed--Muller search error using only Clifford linear preprocessing around the
factored subplan.

The main current limitations are the absence of hardware mapping, the fact that
the exported SSHR-I extension beyond $n\leq 4$ is time-limited rather than an
exact certificate, the fact that ABC/BDD/ESOP/LUT rows are scored through
logic-level estimates rather than full reversible-toolchain synthesis, and the
lack of a reproduced external ROS/mockturtle toolchain in the comparison set.
At $n=16$, the guarded Resource/Profile variants tie their own one-layer
linear-pair child, and the Pareto archive improves that child only modestly, so
the ultra result is bounded scalability evidence plus a residual archive gain
rather than a large new search-quality separation.  The same caution applies even more
strongly at $n=18$, where the guard chooses bounded root-beam search and the
result is a tractability and verification-boundary check rather than evidence
that the full neural portfolio beats its selected child.
The in-harness ESOP cube-beam and weighted-MILP baselines plus the exported
SSHR-I/ABC/BDD/LUT comparisons strengthen the Boolean synthesis comparison, and
the new high-dimensional ABC/BDD/LUT rows show that this external comparison is
no longer restricted to $n\leq 6$.  The $n=16$ and $n=18$ external rows preserve
the weighted-score advantage, but they also keep the ABC-AIG/XAG depth caveat.
More external implementations remain necessary before a submission-ready claim.
The resource-profile sweep shows that objective-specific candidate generation
and non-dominated archive selection improve small-function profile adaptation.
The large benchmark still shows the corresponding high-dimensional tradeoff:
conservative profile guards reduce runtime tails but give up some score.  The
$n=14$ stress test narrows this limitation further: bounded recursive FPRM
linear-pair search keeps the run finite and improves over FPRM-greedy on most
functions, and the $n=15$--$n=16$ scale checks preserve that margin while
showing that Pareto archives can extract small residual gains at substantial
runtime cost.  The remaining weakness is less the internal high-dimensional
guard than the comparison boundary: the current evidence still lacks
reproduced ROS or mockturtle reversible-toolchain
baselines.

\section{Conclusion}

We introduced a logic-level quantum Boolean oracle synthesis method that
combines resource-aware neural MCTS, affine Boolean preconditioning, and a
resource-adaptive portfolio guard.  On the current benchmark, the affine neural
component substantially reduces T-count versus direct ANF, logical-AND direct
ANF, fixed-coordinate MCTS, and SSHR-H on supported functions.  On the
$n\leq 6$ traditional-baseline slice, \paretomethod{} further improves the
balanced weighted score over \method{}, dominates internal ESOP cube-beam
candidates by weighted score, and gives a clear same-benchmark improvement over
both internal ESOP-MILP and exported ABC-ESOP baselines.  Resource-profile and
\largedataset{} benchmarks show that this
advantage is robust across several weighted objectives and larger random ANF
instances.  Exported SSHR, ABC-AIG, ABC-XAG, ABC-LUT, BDD, and ABC-ESOP
baselines add independent cross-tool evidence that the gains
are not an artifact of the internal experiment harness, while also showing that
CNOT and depth remain important limitations.  The new high-dimensional stress
tests show that bounded guards scale without timeouts, beat FPRM-greedy on
60 of 64 weighted-score comparisons at $n=14$ and 30 of 32 comparisons at
$n=15$, complete all 168 $n=16$ ultra-scale rows while retaining score wins
against FPRM root-beam, complete all 84 $n=18$
mega-scale rows under the fast linear-pair guard, and beat exported ABC AIG/XAG/LUT
and BDD on all 528 high-dimensional weighted-score comparisons.
The next step is to reproduce ROS/mockturtle-style
toolchain baselines and hardware-aware mappings so the empirical claim is
submission-ready.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
